---
title: "Crossvalidation I"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

# Estimate and compare four different forms of error i.e.

+ Model errors: from model fits
+ Prediction errors: based on leave-one-out jackknife procedure
+ Hindcast: Retrospective with projection and then compare predictions with observations
+ One-step: Retrospective with leave-one-out for final year 

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
dirMy="/home/laurence/Desktop/sea++/xval"
dirDat=file.path(dirMy,"data")
dirVpa=file.path(dirMy,"inputs/vpa")
dirTex=file.path(dirMy,"tex")
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               fig.width =10, 
               fig.height=8,
               cache     =TRUE, 
               fig.path  ="../tex/xval-vpa-",
               cache.path="../cache/cache-xval-vpa/" 
               )

iFig=0
iTab=0
```

```{r init}
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(ggplotFL)
library(FLCore)
library(diags)
library(stringr)
```

#VPA
```{r source}
source('~/Desktop/flr/diags/R/io.VPA2BoxV2.R')
source('~/Desktop/flr/diags/R/jackknife-vpa2box.R')
source('~/Desktop/flr/diags/R/read-VPA2Box-FLIndices.R')
source('~/Desktop/flr/diags/R/diags-2box.R')
```

```{r data}
nms       =c("FR_AER1","FR_AER2","JPN_LL1_NEA","JPN_LL2_NEA","JPN_LL_EastMed","MOR_POR_TP","MOR_SP_TP","SP_BB1","SP_BB2","WMED_LARV")
names(nms)=c("AS1",     "AS2",   "JPLL_EM",    "JPLL_NEA",   "LJPLL_NEA2",    "MOR1",      "MOR2",     "SpBB1", "SPBB2", "LS")

m=c(0.3800,0.3000,0.2400,0.2000,0.1800,0.1600,0.1400,0.1300,0.1200,0.1000)

vpa=FLStocks("boot"=readVPA2Box(file.path(dirVpa,"ebft/bfte2017.c1"),m=m))
vpa[["fit"]]=run.vpa2box(file.path(dirVpa,"ebft/sims/bfte2017.c1"),m=m)
```

```{r vpa}
plot(vpa)
```
**Figure `r iFig=iFig+1; iFig`**  VPA used for 2017 assessment advice, blue best fit, pink bootstrap with CIs.


```{r diags}
dgs=cbind(error="model",iter=0,diags.vpa2box(file.path(dirVpa,"ebft/sims/MINUS0.R")))
```

```{r jack}
jkVpa=perr.vpa2box(file.path(dirVpa,"ebft/sims/bfte2017.c1"),m=m)
save(jkVpa,file=file.path(dirDat,"jkVpa.RData"),compress="xz")
```

```{r hindcast,eval=FALSE}
file  ="/home/laurence/Desktop/sea++/xval/inputs/vpa/ebft/bfte2017.c1"
dirPrj="/home/laurence/Desktop/sea++/xval/inputs/vpa/ebft/ProjectionsPacth4/6yr"

hc=hindcast(file,dirPrj)
```
\newpage
## Ratio between prediction error and model error
```{r err-ratio}
d1=ddply(jkVpa[[2]], .(name),with,data.frame(p.error=var(p.error )^0.5))
d2=ddply(dgs,        .(name),with,data.frame(m.error=var(residual)^0.5))
transform(data.frame(d1,m.error=d2[,"m.error"]),ratio=p.error/m.error)
```

```{r err-m}
ggplot(dgs)+geom_boxplot(aes(name,residual))+
  theme_bw()+
  theme(axis.text.x=element_text(size=20, angle=90, vjust=0.8))
```
**Figure `r iFig=iFig+1; iFig`**  Distribution of model error.

```{r err-p}
ggplot(jkVpa[[2]])+geom_boxplot(aes(name,p.error))+
  theme_bw()+
  theme(axis.text.x=element_text(size=20, angle=90, vjust=0.8))
```
**Figure `r iFig=iFig+1; iFig`**  Distribution of prediction error.

```{r er-mp}
ggplot()+
  geom_point(aes(as.integer(ac(year)),p.error),col="red",data=jkVpa[[2]])+
  geom_point(aes(year,residual),data=as.data.frame(dgs))+
  facet_wrap(~name,ncol=3)+
  theme_bw(16)
```
**Figure `r iFig=iFig+1; iFig`**  Comparison of prediction (red) and model error.

```{r ss}
load(file.path(dirDat,"jk_atl_bftSS3.RData"))

names(cpues)[-1]=c("index","name","year","season","obs","hat","use")
names(sacpue)=c("index","name","year","season","obs","hat","use")
cpues=subset(cpues,use==-1)
```

#SS
## Ratio between prediction error and model error
\newpage
```{r ss-err-ratio}
d1=ddply(cpues, .(name),with,data.frame(p.error=var(log(obs/hat),na.rm=TRUE)^0.5))
d2=ddply(sacpue,.(name),with,data.frame(m.error=var(log(obs/hat),na.rm=TRUE)^0.5))

transform(data.frame(d1,m.error=d2[,"m.error"]),ratio=p.error/m.error,
                                                name =nms[name])
```

```{r ss-err-m}
ggplot(transform(sacpue,name=nms[name]))+
  geom_boxplot(aes(name,log(obs/hat)))+
  theme_bw()+
  theme(axis.text.x=element_text(size=20, angle=90, vjust=0.8))
```
**Figure `r iFig=iFig+1; iFig`**  Distribution of model error.

```{r ss-err-p}
ggplot(transform(cpues,name=nms[name]))+
  geom_boxplot(aes(name,log(obs/hat)))+
  theme_bw()+
  theme(axis.text.x=element_text(size=20, angle=90, vjust=0.8))
```
**Figure `r iFig=iFig+1; iFig`**  Distribution of prediction error.

```{r ss-er-mp}
ggplot()+
  geom_point(aes(year,log(obs/hat)),col="red",data=transform(cpues,name=nms[name]))+
  geom_point(aes(year,log(obs/hat)),          data=transform(sacpue,name=nms[name]))+
  facet_wrap(~name,ncol=3)+
  theme_bw()+
  theme(axis.text.x=element_text(size=20, angle=90, vjust=0.8))
```
**Figure `r iFig=iFig+1; iFig`**  Comparison of prediction (red) and model error.

```{r errors}
save(sacpue,cpues,jkVpa,dgs,file="/home/laurence/Desktop/tmp/tmp.RData")

rsd=rbind(transmute(cpues,     name=nms[name],error=log(obs/hat),method="SS",type="prediction"),
          transmute(sacpue,    name=nms[name],error=log(obs/hat),method="SS",type="model"),
          transmute(jkVpa[[2]],name=name,     error=p.error,     method="VPA",type="prediction"),
          transmute(dgs,       name=name,     error=residual,    method="VPA",type="model"))

ggplot(rsd)+
  geom_boxplot(aes(type,error,fill=type))+
  theme_bw(16)+
  theme(axis.text.x=element_text(size=10, angle=90, vjust=0.8),legend.position = "bottom")+
  facet_grid(method~name)

```
**Figure `r iFig=iFig+1; iFig`**  Comparison of prediction (red) and model error by series for SS and VPA.


#Hindcasts
##VPA

```{r indices}
idx=readVPA2BoxIndices(file.path(dirVpa,"ebft/sims/bfte2017.d1"))

ggplot(ldply(idx,function(x) as.data.frame(index(x))))+
  geom_line(aes(year,data))+
  facet_grid(.id~.,scale="free_y")+
  xlab("Year")+ylab("CPUE")
```
**Figure `r iFig=iFig+1; iFig`**  CPUE series


```{r retros}
dirs=c(file.path(dirVpa,"ebft/sims"),
       file.path(dirVpa,"ebft/sims/2016"),
       file.path(dirVpa,"ebft/sims/2015"),
       file.path(dirVpa,"ebft/sims/2014"),
       file.path(dirVpa,"ebft/sims/2013"),
       file.path(dirVpa,"ebft/sims/2012"),
       file.path(dirVpa,"ebft/sims/2011"))
xfls=file.path(dirs,"bfte2017.c1")

vpaRetro=FLStocks(mlply(xfls,readVPA2Box,m=m))
names(vpaRetro)=ac(seq(2017:2011))
plot(vpaRetro)
```
**Figure `r iFig=iFig+1; iFig`**  Retrospectives


```{r jk1}
jkVpas=list("2017"=jackknife.vpa2box(xfls[[1]],m=m))
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```

```{r jk2}
jkVpas[["2016"]]=jackknife.vpa2box(xfls[[2]],m=m)
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```

```{r jk3}
jkVpas[["2015"]]=jackknife.vpa2box(xfls[[3]],m=m)
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```

```{r jk4}
jkVpas[["2014"]]=jackknife.vpa2box(xfls[[4]],m=m)
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```

```{r jk5}

jkVpas[["2013"]]=jackknife.vpa2box(xfls[[5]],m=m)
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```

```{r jk6}
jkVpas[["2012"]]=jackknife.vpa2box(xfls[[6]],m=m)
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```

```{r jk7}
jkVpas[["2011"]]=jackknife.vpa2box(xfls[[7]],m=m)
```

```{r}
save(jkVpas,file=file.path(dirDat,"jkVpas.RData"),compress="xz")
```
