---
title: "Bluefin" 
subtitle: "Runs"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown:::pdf_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
  

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =!FALSE,
               cache.path="../cache/om/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/om-")

iFig=0
```
```{r, pkgs, echo=FALSE, message=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)

library(GGally)
library(corrplot)

library(qicharts2)

library(ggplotFL)
library(FLRP)
library(diags)
library(r4ss)
library(ss3om)

library(gam)

options(digits=3)
```
```{r, dirs, echo=FALSE, message=FALSE}
dirMy=dirname(dirname(FLife:::getScriptPath()))
dirInp="/home/laurence/Desktop/sea++/xval/inputs/ss"
dirDat=file.path(dirMy,"data")
dirBase=file.path(dirInp,"base")
```


```{r, data-stk}
om=FLStocks(mlply(expand.grid(run=c("run59","run82"),scen=c("base","aspm","aspm-rec")), 
                function(run,scen) readFLSss3(file.path(dirInp,run,scen))))
```

```{r, dgs}
source('~/Desktop/flr/diags/R/diags-SS.R')

diagsFn=diags:::diagsFn

dgs=mdply(expand.grid(run=c("run59","run82"),scen=c("base","aspm","aspm-rec")), 
                function(run,scen) .diagUss(file.path(dirInp,run,scen)))

qgs=ddply(dgs,.(run,scen), with, 
          {res=qic(year,residual,facet=~name,chart="i")$data
          attributes(res)$class="data.frame"
          res})
```

\newpage
# Figures
```{r, flstock, fig.height=9}
theme_set(theme_bw())

ggplot(ldply(om,function(x) plot(x)$data))+
  geom_line(aes(year,data,col=scen))+
  facet_grid(qname~run,scale="free")+
  xlab("Year")+ylab("")+
  guides(col=guide_legend(title="Scenario"))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`** Time series of recruitment, SSB, catch and fishing mortality.


\begin{landscape}
```{r, residuals, fig.width=10,fig.height=8}
theme_set(theme_bw())

ggplot(aes(x,y,col=scen),data=qgs)+
  geom_point()+
  geom_smooth(se=FALSE,span=1)+
  facet_grid(run~facet1,scale="free",space="free")+
    theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_continuous(breaks=seq(1950,2010,10))
```

**Figure `r iFig=iFig+1; iFig`** Residuals
\end{landscape}

## Software
All analysis was conducted using R and FLR and the `diags` package which provides a set of common methods for reading these data into R, plotting and summarising them.(http://www.flr-project.org/)

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* diags: `r # packageVersion('diags')`
* ggplotFL: `r # packageVersion('ggplotFL')`
* diags: `r # packageVersion('diags')`
* r4ss: `r # packageVersion('r4ss')`

* **Compiled**: `r date()`

## Author information

**Laurence KELL**. laurie@kell.es

# References {#References}