---
title: "Performance of model selection and diagnosis by cross-validation: evaluation by simulation"
subtitle: "Operation Model"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

# Operating model to simulate 3 contrasting stocks
+ Atlantic bigeye tuna
+ North East Atlantic Skate
+ Irish Sea sprat
+ Plaice

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
dirMy="/home/laurence/Desktop/sea++/xval"
dirDat=file.path(dirMy,"data")
dirVpa=file.path(dirMy,"inputs/vpa")
dirTex=file.path(dirMy,"tex")
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/xval2-om",
               cache.path="../cache/xval2-om/" 
               )

iFig=0
iTab=0
```

```{r libs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(ggplotFL)
library(FLife)
```

## Life history parameters

```{r lh}
load("/home/laurence/Desktop/sea++/mydas/tasks/data/fishbase-web.RData")

names(fb)[c(14,17)]=c("l50","a50")
fb=fb[,c("species","linf","k","t0","a","b","a50","l50")]

ray   =subset(fb,species=="Raja clavata")
sprat =subset(fb,species=="Sprattus sprattus sprattus")
bigeye=subset(fb,species=="Thunnus obesus")
plaice=plaice=subset(fb,species=="Pleuronectes platessa")
```

```{r}
my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_point(...,size=.5)+
  geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_density(...,lwd=1)}

theme_set(theme_bw(base_size=20))

p=ggpairs(transform(rbind(ray,sprat,bigeye,plaice),
                    species=factor(ac(species)),linf=log(linf),k=log(k),l50=log(l50)),
  mapping = ggplot2::aes(color=species),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

```{r parSprat}
theme_set(theme_bw(base_size=20))

ggpairs(transform(sprat[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of sprat life history parameters.

```{r parBigeye}
theme_set(theme_bw(base_size=20))

ggpairs(transform(bigeye[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of bigeye life history parameters.

```{r parRay}
theme_set(theme_bw(base_size=20))

ggpairs(transform(ray[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of thornback ray life history parameters.


```{r parPlaice}
theme_set(theme_bw(base_size=20))

ggpairs(transform(plaice[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of plaice life history parameters.

## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r eql}
source('~/Desktop/flr/FLife/R/lhPar.R')

sim<-function(x,niters=500,se=0.3){
  
  mn=aaply(x,1,mean, na.rm=TRUE)
  sd=aaply(x,1,var,  na.rm=TRUE)^0.5
  n =aaply(x,1,function(x) sum(!is.na(x)))
  se=sd/n^0.5
  
  if (any(is.na(se)))
    se[is.na(se)]=mn[is.na(se)]*se
  
  y=data.frame(mn=mn,se=se)
  y=mdply(y,function(mn,se) rnorm(niters,mn,se))[,-(1:2)]
  
  res=FLPar(array(unlist(c(y)),c(dim(x)[1],niters)))
  
  dimnames(res)$params=names(mn)

  res}

# create FLPar
lhRay   =mf2FLPar(ray[,   -c(1)])
lhSprat =mf2FLPar(sprat[, -c(1,7:8)])
lhBigeye=mf2FLPar(bigeye[,-c(1,7:8)])
lhPlaice=mf2FLPar(plaice[,-c(1)])

# Monte Carlo
lhRay   =sim(lhRay)
lhSprat =sim(lhSprat)
LhBigeye=sim(lhBigeye)
LhPlaice=sim(lhPlaice)

# create FLPar
lhRay   =lhPar(lhRay)
lhSprat =lhPar(lhSprat[, -c(7:8)])
lhBigeye=lhPar(lhBigeye[,-c(7:8)])
lhPlaice=lhPar(lhPlaice[,-c(7:8)])

# equilibium dynamics
eqlRay   =lhEql(lhRay)
eqlSprat =lhEql(lhSprat)
eqlBigeye=lhEql(lhBigeye)
eqlPlaice=lhEql(lhPlaice)
```

```{r eqlSave}
save(lhRay,  lhSprat, lhBigeye, lhPlaice,file=file.path(dirDat,"xval2_lh.RData"))
save(eqlRay,eqlSprat,eqlBigeye,eqlPlaice, file=file.path(dirDat,"xval2_eql.RData"))
```

```{r vectorRay}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

dat=FLQuants(eqlRay,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors for thornback ray.

```{r vectorSprat}
dat=FLQuants(eqlSprat,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
  
```

**Figure `r iFig=iFig+1; iFig`** Vectors for sprat.

```{r vectorBigye}
dat=FLQuants(eqlBigeye,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors for bigeye.


```{r vectorPlaice}
dat=FLQuants(eqlPlaice,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors for Plaice.

## Population dynamics

```{r omRay}
omRay=fwd(eqlRay)

plot(omRay)
```

**Figure `r iFig=iFig+1; iFig`** Time series for thornback ray.

```{r omSprat}
library(FLash)
source('~/Desktop/flr/FLash/R/fwd.R')
source('~/Desktop/flr/FLash/R/fwdControl.R')

omSprat=fwd(eqlSprat,maxF=5)

plot(omSprat)
```

**Figure `r iFig=iFig+1; iFig`** Time series for sprat.

```{r omBigeye}
omBigeye=fwd(eqlBigeye)

plot(omBigeye)
```

**Figure `r iFig=iFig+1; iFig`** Time series for bigeye.


```{r omPlaice}
omPlaice=fwd(eqlPlaice)

plot(omPlaice)
```

**Figure `r iFig=iFig+1; iFig`** Time series for plaice.


```{r omSave}
save(omRay,omSprat,omBigeye,omPlaice,file=file.path(dirDat,"xval2_om.RData"),compress="xz")
```


## Fleets

```{r fleets}
```


## Scenarios

```{r scen}
```

## Projections

```{r}
```

