---
title: "Performance of model selection and diagnosis by cross-validation: evaluation by simulation"
subtitle: "Operation Model"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

# Operating model to simulate 3 contrasting stocks
+ Atlantic bigeye tuna
+ North East Atlantic Skate
+ Irish Sea sprat

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
dirMy="/home/laurence/Desktop/sea++/xval"
dirDat=file.path(dirMy,"data")
dirVpa=file.path(dirMy,"inputs/vpa")
dirTex=file.path(dirMy,"tex")
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/xval-om-",
               cache.path="../cache/xval-om/" 
               )

iFig=0
iTab=0
```

```{r libs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)

library(FLCore)
library(ggplotFL)
library(FLife)
```

## Life history parameters

```{r lh}
load("/home/laurence/Desktop/sea++/mydas/tasks/data/fishbase-web.RData")

names(fb)[c(14,17)]=c("a50","l50")
fb=fb[,c("species","linf","k","t0","a","b","a50","l50")]

ray   =subset(fb,species=="Raja clavata")
sprat =subset(fb,species=="Sprattus sprattus sprattus")
bigeye=subset(fb,species=="Thunnus obesus")
sole  =subset(fb,substr(species,1,3)=="Sol")
plaice=subset(fb,substr(species,1,3)=="Pla")
```

```{r}
library(GGally)

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_point(...,size=.5)+
  geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_density(...,lwd=1)}

theme_set(theme_bw(base_size=20))


ggpairs(transform(rbind(ray,sprat,bigeye),species=factor(ac(species)),linf=log(linf),k=log(k),l50=log(l50)),
  mapping = ggplot2::aes(color=species),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of life history parameters.

```{r}
theme_set(theme_bw(base_size=20))

ggpairs(transform(subset(lh,species=="Sprattus sprattus sprattus")[,-1],
                  linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of sprat life history parameters.

```{r}
theme_set(theme_bw(base_size=20))

ggpairs(transform(subset(lh,species=="Thunnus obesus")[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of bigeye life history parameters.

```{r}
theme_set(theme_bw(base_size=20))

ggpairs(transform(subset(lh,species=="Raja clavata")[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of thornback ray life history parameters.


## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r eql}
source('~/Desktop/flr/FLife/R/lhPar.R')

sim<-function(x,niters=500,se=0.3){
  
  mn=aaply(x,1,mean, na.rm=TRUE)
  sd=aaply(x,1,var,  na.rm=TRUE)^0.5
  n =aaply(x,1,function(x) sum(!is.na(x)))
  se=sd/n^0.5
  
  if (any(is.na(se)))
    se[is.na(se)]=mn[is.na(se)]*se
  
  y=data.frame(mn=mn,se=se)
  y=mdply(y,function(mn,se) rnorm(niters,mn,se))[,-(1:2)]
  
  res=FLPar(array(unlist(c(y)),c(dim(x)[1],niters)))
  
  dimnames(res)$params=names(mn)

  res}

# create FLPar
rayLh   =mf2FLPar(ray[,   -c(1)])
spratLh =mf2FLPar(sprat[, -c(1,7:8)])
bigeyeLh=mf2FLPar(bigeye[,-c(1,7:8)])

# Monte Carlo
rayLh  =sim(rayLh)
spratLh=sim(spratLh)
bigeyLh=sim(bigeyeLh)

# create FLPar
rayLh   =lhPar(rayLh)
spratLh =lhPar(spratLh[, -c(7:8)])
bigeyeLh=lhPar(bigeyeLh[,-c(7:8)])

# equilibium dynamics
eqlRay   =lhEql(rayLh)
eqlSprat =lhEql(spratLh)
eqlBigeye=lhEql(bigeyeLh)
```

```{r vectorRay}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

dat=FLQuants(eqlRay,"m","catch.sel"=sel,"mat","catch.wt")

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,20))
```

**Figure `r iFig=iFig+1; iFig`** Vectors for thornback ray.

```{r vectorSprat}
dat=FLQuants(eqlSprat,"m","catch.sel"=sel,"mat","catch.wt")

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,20))
  
```

**Figure `r iFig=iFig+1; iFig`** Vectors for sprat.

```{r vectorBigye}
dat=FLQuants(eqlBigeye,"m","catch.sel"=sel,"mat","catch.wt")

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,20))
```

**Figure `r iFig=iFig+1; iFig`** Vectors for bigeye.

## Population dynamics

```{r omRay}
omRay=fwd(eqlRay)
```

```{r omSprat}
omSprat=fwd(eqlSprat)
```

```{r omBigeye}
omBigeye=fwd(eqlBigeye)
```

## Fleets

```{r fleets}
```


## Scenarios

```{r scen}
```

## Projections

```{r}
```

**Figure `r iFig=iFig+1; iFig`**  VPA used for 2017 assessment advice, blue best fit, pink bootstrap with CIs.
