---
title: "Performance of model selection and diagnosis by cross-validation: evaluation by simulation"
subtitle: "Conditioning of Operating Model"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

# Operating model to simulate 4 contrasting stocks
+ Atlantic bigeye tuna
+ Thornback Ray
+ Sprat
+ Plaice

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
dirMy="/home/laurence/Desktop/sea++/xval"
dirDat=file.path(dirMy,"data")

nits=500
```



```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/xval2-om",
               cache.path="../cache/xval2-om/" 
               )

iFig=0
iTab=0
```

```{r libs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(ggplotFL)
library(FLife)
```

```{r, source, eval=FALSE}
source('~/Desktop/flr/FLBRP/R/fwd.R')
source('~/Desktop/flr/FLash/R/fwd.R')
source('~/Desktop/flr/FLash/R/fwdControl.R')
source('~/Desktop/flr/FLife/R/generic.R')
source('~/Desktop/flr/FLife/R/lopt.R')
source('~/Desktop/flr/FLife/R/lhPar.R')
```

## Life history parameters

```{r lh}
load("/home/laurence/Desktop/sea++/mydas/tasks/data/fishbase-web.RData")

names(fb)[c(14,17)]=c("l50","a50")
fb=fb[,c("species","linf","k","t0","a","b","a50","l50")]

ray   =subset(fb,species=="Raja clavata")
sprat =subset(fb,species=="Sprattus sprattus sprattus")
bigeye=subset(fb,species=="Thunnus obesus")
plaice=plaice=subset(fb,species=="Pleuronectes platessa")
```

```{r devs}
set.seed(1233)
srDev=FLife:::rlnoise(nits,FLQuant(0,dimnames=list(year=1:100)),.5,b=0.0)
```

```{r}
my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_point(...,size=.5)+
  geom_smooth(...,method="lm",se=FALSE)}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
  geom_density(...,lwd=1)}

theme_set(theme_bw(base_size=20))

p=ggpairs(transform(rbind(ray,sprat,bigeye,plaice),
                    species=factor(ac(species)),linf=log(linf),k=log(k),l50=log(l50)),
  mapping = ggplot2::aes(color=species),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

```{r parSprat}
theme_set(theme_bw(base_size=20))

ggpairs(transform(sprat[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of sprat life history parameters.

```{r parBigeye}
theme_set(theme_bw(base_size=20))

ggpairs(transform(bigeye[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of bigeye life history parameters.

```{r parRay}
theme_set(theme_bw(base_size=20))

ggpairs(transform(ray[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of thornback ray life history parameters.


```{r parPlaice}
theme_set(theme_bw(base_size=20))

ggpairs(transform(plaice[,-1],linf=log(linf),k=log(k),l50=log(l50)),
  lower = list(continuous = wrap(my_smooth)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+
  theme(legend.position ="none",
  panel.grid.major =element_blank(),
  axis.ticks       =element_blank(),
  axis.text.x      =element_blank(),
  axis.text.y      =element_blank(),
  panel.border     =element_rect(linetype = 1, colour="black", fill=NA))
```

**Figure `r iFig=iFig+1; iFig`** Pairwise scatter plots of plaice life history parameters.

## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r eql}
sim<-function(x,niters=500,se=0.3){
  
  mn=aaply(x,1,mean, na.rm=TRUE)
  sd=aaply(x,1,var,  na.rm=TRUE)^0.5
  n =aaply(x,1,function(x) sum(!is.na(x)))
  se=sd/n^0.5
  
  if (any(is.na(se))) se[is.na(se)]=se
  
  y=data.frame(mn=mn,se=se)
  y=mdply(y,function(mn,se) rnorm(niters,mn,se))[,-(1:2)]
  
  res=FLPar(array(unlist(c(y)),c(dim(x)[1],niters)))
  
  dimnames(res)$params=names(mn)

  res}

# create FLPar
lhRay   =FLife:::mf2FLPar(ray[,   -c(1)])
lhSprat =FLife:::mf2FLPar(sprat[, -c(1,7:8)])
lhBigeye=FLife:::mf2FLPar(bigeye[,-c(1,7:8)])
lhPlaice=FLife:::mf2FLPar(plaice[,-c(1)])

# Monte Carlo
lhRay   =sim(lhRay,niters=nits)
lhSprat =sim(lhSprat,niters=nits)
lhBigeye=sim(lhBigeye,niters=nits)
lhPlaice=sim(lhPlaice,niters=nits)

# create FLPar
lhRay   =lhPar(lhRay)
lhSprat =lhPar(lhSprat[, -c(7:8)])
lhBigeye=lhPar(lhBigeye[,-c(7:8)])
lhPlaice=lhPar(lhPlaice[,-c(7:8)])

# equilibium dynamics
eqlRay   =lhEql(lhRay)
eqlSprat =lhEql(lhSprat)
eqlBigeye=lhEql(lhBigeye)
eqlPlaice=lhEql(lhPlaice)

```

```{r eqlSave}
save(lhRay,  lhSprat, lhBigeye, lhPlaice,file=file.path(dirDat,"xval2_lh.RData"),compress="xz")
save(eqlRay,eqlSprat,eqlBigeye,eqlPlaice, file=file.path(dirDat,"xval2_eql.RData"),compress="xz")
```

```{r vectorRay}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

dat=FLQuants(eqlRay,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors for thornback ray.

```{r vectorSprat}
dat=FLQuants(eqlSprat,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975),na.rm=TRUE)),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
  
```

**Figure `r iFig=iFig+1; iFig`** Vectors for sprat.

```{r vectorBigye}
dat=FLQuants(eqlBigeye,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors for bigeye.


```{r vectorPlaice}
dat=FLQuants(eqlPlaice,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Mass"=stock.wt)

res=ldply(dat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Vectors for Plaice.

## Population dynamics

```{r omRay}
#http://www.fishbase.org/manual/Key%20Facts.htm

gTime=round(FLife:::genTime(FLPar(aaply(lhRay,1,mean))))

FLBRP:::fbar(eqlRay)=FLBRP:::refpts(eqlRay)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                                                 seq(.1,2,length.out=40),
                                                                 seq(2,.7,length.out=gTime)[-1],
                                                                 rep(.7,61)))

omRay=fwd(eqlRay)
omRay=fwd(omRay,f=fbar(omRay)[,-1],sr=eqlRay,sr.residuals=srDev)

plot(omRay)
```

**Figure `r iFig=iFig+1; iFig`** Time series for thornback ray.

```{r omSprat}
gTime=round(FLife:::genTime(FLPar(aaply(lhSprat,1,mean))))

FLBRP:::fbar(eqlSprat)=FLBRP:::refpts(eqlSprat)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                                         seq(.1,2,length.out=40),
                                                         seq(2,.7,length.out=gTime)[-1],
                                                         rep(.7,61)))[,1:100]
omSprat=fwd(eqlSprat,maxF=5)
omSprat=fwd(omSprat,f=fbar(omSprat)[,-1],sr=eqlSprat) #,sr.residuals=srDev,maxF=5)

plot(omSprat)
```

**Figure `r iFig=iFig+1; iFig`** Time series for sprat.

```{r omBigeye}
gTime=round(FLife:::genTime(FLPar(aaply(lhBigeye,1,mean))))

FLBRP:::fbar(eqlBigeye)=FLBRP:::refpts(eqlBigeye)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                                         seq(.1,2,length.out=40),
                                                         seq(2,.7,length.out=gTime)[-1],
                                                         rep(.7,61)))[,1:100]
omBigeye=fwd(eqlBigeye)
omBigeye=fwd(omBigeye,f=fbar(omBigeye)[,-1],sr=eqlBigeye,sr.residuals=srDev[,,,,,dimnames(m(omBigeye))$iter])

plot(omBigeye)
```

**Figure `r iFig=iFig+1; iFig`** Time series for bigeye.


```{r omPlaice}
gTime=round(FLife:::genTime(FLPar(aaply(lhPlaice,1,mean))))

FLBRP:::fbar(eqlPlaice)=FLBRP:::refpts(eqlPlaice)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                                         seq(.1,2,length.out=40),
                                                         seq(2,.7,length.out=gTime)[-1],
                                                         rep(.7,61)))[,1:100]
omPlaice=fwd(eqlPlaice)
omPlaice=fwd(omPlaice,f=fbar(omPlaice)[,-1],sr=eqlPlaice,sr.residuals=srDev[,,,,,dimnames(m(eqlPlaice))$iter])

plot(omPlaice)
```

**Figure `r iFig=iFig+1; iFig`** Time series for plaice.

```{r omSave}
save(omRay,omSprat,omBigeye,omPlaice,file=file.path(dirDat,"xval2_om.RData"),compress="xz")
```

## Fleets

```{r sel-ray, fig.height=4}
selRay              =FLQuants("Adult"=dnormal(ages(catch.sel(eqlRay)),lhRay[c("a1","sl","sr")]))
selRay[["Juvenile"]]=1-selRay[["Adult"]]
selRay[["Domed"]]   =dnormal(ages(catch.sel(eqlRay)),rbind(lhRay[c("a1","sl")],FLPar(sr=5)))

res=ldply(selRay,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Selection patterns for thornback ray.


```{r sel-sprat, fig.height=4}
selSprat              =FLQuants("Adult"=dnormal(ages(catch.sel(eqlSprat)),lhSprat[c("a1","sl","sr")]))
selSprat[["Juvenile"]]=1-selSprat[["Adult"]]
selSprat[["Domed"]]   =dnormal(ages(catch.sel(eqlSprat)),rbind(lhSprat[c("a1","sl")],FLPar(sr=5)))

res=ldply(selSprat,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Selection patterns for Sprat.



```{r sel-bigeye, fig.height=4}
selBigeye              =FLQuants("Adult"=dnormal(ages(catch.sel(eqlBigeye)),lhBigeye[c("a1","sl","sr")]))
selBigeye[["Juvenile"]]=1-selBigeye[["Adult"]]
selBigeye[["Domed"]]   =dnormal(ages(catch.sel(eqlBigeye)),rbind(lhBigeye[c("a1","sl")],FLPar(sr=5)))

res=ldply(selBigeye,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Selection patterns for bigeye.


```{r sel-plaice, fig.height=4}
selPlaice              =FLQuants("Adult"=dnormal(ages(catch.sel(eqlPlaice)),lhPlaice[c("a1","sl","sr")]))
selPlaice[["Juvenile"]]=1-selPlaice[["Adult"]]
selPlaice[["Domed"]]   =dnormal(ages(catch.sel(eqlPlaice)),rbind(lhPlaice[c("a1","sl")],FLPar(sr=5)))

res=ldply(selPlaice,function(x) cast(as.data.frame(quantile(x,probs=c(0.025,0.25,0.5,0.75,0.975))),
                               age~iter,value="data"))

ggplot(res)+
  geom_ribbon(aes(age,ymin=`25%`,ymax=`75%`),alpha=0.5,fill="red")+
  geom_ribbon(aes(age,ymin=`2.5%`,ymax=`97.5%`),alpha=0.1,fill="red")+
  geom_line(aes(age,`50%`))+
  facet_wrap(~.id,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")
```

**Figure `r iFig=iFig+1; iFig`** Selection patterns for plaice.

```{r saveSel}
save(selRay,selSprat,selBigeye,selPlaice,file=file.path(dirDat,"sel.RData"),compress="xz")
```


## Scenarios

```{r scen}
```
