---
title: "North Atlantic Albacore MSE"
subtitle: "Exploratory Analysis"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

Looking at a single OM for a range of MP options, or a single MP for a range of OM scenarios it is easier to understand how the MSE are performing. It is also helpful to look at a single iteration, since this helps to check if bounds and other feedback elements are working as expected. For example **Figure 1** shows results for a single OM and MP scenario with bounds of 20, 25 and 30%, it would be expected that as a bound becomes more restrictive i.e. reduces from 30 to 20%, variability in catches would be reduced and that for a stock currentky below $B_{MSY}$ that in the short term F would be higher and SSB lower than the case with a bound of 30%. **Figure 2** shows the same scenarios for a single iteration.

**Figure 3** Shows the medians by $B_{threshold}$ (row) and $F_{target}$ (lines, the red line is for an $F_{target}$ of 0.8) for a TAC bound of 30%. 


**Figures 4** and **5** contrast the same OM for different values of steepness.  

The plots, although quite simple need some explaining, e.g.

*    you can not compare runs as the random numbers vary by scenario.
*    Fig 1 is troubling, you would expect the 25% bound to be intermediate to the 20 and 30% bounds.
*    Recruitment (and CV of OEM) could be a bigger determinant of outcome than the MP
*    Steepness appears to have no effect

## Agreed validation steps before any advice will be given

*  Use the same random deviates across all scenarios, and check stability of higher and lower percentiles within and across OM/MP scenarios. i.e. run for 1000 iters for selected OM/MP combinations.
*  To check SRR run with high F’s and the dynamics are working the way they should, i.e contrast in the Spawning stock size and what it gives on recruitment
*  Conduct a crosstest, i.e. run OM without feedback generate catch and CPUE fit SA, every 3 years and compare the OM and stock assessment (SA)
*  Use OEM in cross test
*  For all OM/MP trials run simple F=Ftarget projection, to check dynamics
*  Run OM with feedback for an F target of FMSY  and compare to F projection
*  Run a OM with feedback for an F target of FMSY and an Btreshold of BMSY, compare to above.
*  Run a OM with feedback for an F target of FMSY and an Btreshold of BMSY plus TAC bounds of 20, 25 and 30%, compare to above.
*  Run scenarios using a factorial design, i.e. main effects, 1st, 2nd, ... order interactions, see if you can predict the performance indicators
*  Compare OM and MP reference points
*  Check TAC output by MP and Catch taken from OM, iteration by iteration.
*  OM conditioning, of historic and future, i.e. calculate the OM production functions and compare trajectories to these. 
*  Compare OM reference points and statistics such as K, r, … to MP values 
*  Check SA, e.g. hitting bounds, convergence
*  Compare TAC output from MP compared to Catch from OM


```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               fig.width =10, 
               fig.height=8,
               fig.path  ="../tex/om-")
iFig=0
iTab=0
```

```{r init}
library(plyr)
library(dplyr)
library(stringr)
library(reshape2)
library(ggplot2)
library(ggplotFL)
library(FLCore)
library(FLBRP)

dirMy ="/home/laurie/Desktop/MEGAsync/mse/albn"
dirTex=file.path(dirMy,"tex")
dirDat=file.path(dirMy,"data")
dirInp=file.path(dirMy,"inputs")

load("/home/laurie/Desktop/MEGAsync/mse/albn/data/key.RData")

dirMedia="/media/laurie/FREECOM HDD/nalbMse"
```

```{r funcs}
FLQuants2FLQuant<-function(object){
   mat=ldply(object,as.data.frame)[,-7]
   names(mat)[1]="iter"
   mat$iter=as.numeric(as.factor((mat$iter)))
   
   as.FLQuant(mat)}
 
 flqs2flq<-function(object,flq){
   nit=laply(object,function(x) dims(x)$iter)
   nit=c(0,cumsum(nit))[seq(length(nit))]
   
    mat=mdply(seq(length(nit)),function(i) {
     transform(as.data.frame(slot(object[[i]],flq)),
               iter=as.numeric(as.character(iter))+nit[i])})[,-1]
   
   as.FLQuant(mat)}

FLStocks2FLStock<-function(object){
  dms=ldply(object,function(x) unlist(dims(x)))

  dms$min=as.numeric(dms$min)
  dms$max=as.numeric(dms$max)
  dms$minyear=as.numeric(dms$minyear)
  dms$maxyear=as.numeric(dms$maxyear)

  dmns=list(age =min(dms$min):max(dms$max),
            year=min(dms$minyear):max(dms$maxyear))

  nts=length(object)
  res=propagate(FLStock(catch.n=FLQuant(NA,dimnames=dmns)),nts)

  minyear=unique(laply(object,function(x) dims(x)$minyear))
  if (length(minyear)>1)
    object=FLStocks(llply(object,window,start=min(minyear)))

  slt=getSlots("FLStock")
  for (s in names(slt[slt%in%"FLQuant"]))
    slot(res,s)=flqs2flq(object,s)

  units(harvest(res))=units(harvest(object[[1]]))

  res}
```


```{r om1}
load(file.path(dirMedia,"MSE_hcr_om1_hcr1_bounded20.RData"))
oms=FLStocks("20"=window(MSE_hcr$om,end=2044))
load(file.path(dirMedia,"MSE_hcr_om1_hcr1_bounded25.RData"))
oms[["25"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr1_bounded30.RData"))
oms[["30"]]=window(MSE_hcr$om,end=2044)
```


```{r om1-plot}
p=plot(oms)+
  theme_bw()
p$data=subset(p$data,year>2000)
p
```
**Figure `r iFig=iFig+1; iFig`.** Operating Model runs for Multifan-CL scenario Alt1 with M=0.2 and steepness=0.6; HCR with Ftarget=0.6 and Bthreshold=0.6.


```{r om1-plot2}
plot(FLStocks(llply(oms,function(x) window(iter(x,1),start=2000))))+
  geom_vline(aes(xintercept=2014))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** Single iteration for Operating Model runs for Multifan-CL scenario Alt1 with M=0.2 and steepness=0.6; HCR with Ftarget=0.6 and Bthreshold=0.6.

```{r}
load(file.path(dirMedia,"MSE_hcr_om1_hcr1_bounded30.RData"))
oms=FLStocks("1"=window(MSE_hcr$om,end=2044))
load(file.path(dirMedia,"MSE_hcr_om1_hcr2_bounded30.RData"))
oms[["2"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr3_bounded30.RData"))
oms[["3"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr4_bounded30.RData"))
oms[["4"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr5_bounded30.RData"))
oms[["5"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr6_bounded30.RData"))
oms[["6"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr7_bounded30.RData"))
oms[["7"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr8_bounded30.RData"))
oms[["8"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr9_bounded30.RData"))
oms[["9"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr10_bounded30.RData"))
oms[["10"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr11_bounded30.RData"))
oms[["11"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr12_bounded30.RData"))
oms[["12"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr13_bounded30.RData"))
oms[["13"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr14_bounded30.RData"))
oms[["14"]]=window(MSE_hcr$om,end=2044)
load(file.path(dirMedia,"MSE_hcr_om1_hcr15_bounded30.RData"))
oms[["15"]]=window(MSE_hcr$om,end=2044)

mp=subset(key,om==1&bound==30&steepness=="h6"&m=="M02")
p=plot(FLStocks(llply(oms,function(x) iter(window(x,start=2015),1:100))))

p$data=transform(p$data,
                  threshold=mp[stock,"btrig"],
                  target   =mp[stock,"ftar"])
names(p$data)[9:11]=c("10%","50%","90%")
ggplot(p$data)+
  #geom_ribbon(aes(year,ymax=`90%`,ymin=`10%`,fill=factor(target)),alpha=.05)+
  geom_line(  aes(year,y=`50%`,group=factor(target)))+
  geom_line(  aes(year,y=`50%`,group=factor(target)),data=subset(p$data,target==.8),col="red")+
  facet_grid(qname~threshold,scale="free")+
  theme_bw()+
  xlab("Year")+ylab("Median")
```
**Figure `r iFig=iFig+1; iFig`.** Median for Operating Model runs for Multifan-CL scenario Alt1 with M=0.2 and steepness=0.6; bound=30%.

```{r}
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M02"&q=="q0"&bound==30)[1,"file"]))
oms=FLStocks("h6"=MSE_hcr$om)
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M02"&q=="q0"&bound==30)[2,"file"]))
oms[["h7"]]=MSE_hcr$om
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M02"&q=="q0"&bound==30)[3,"file"]))
oms[["h8"]]=MSE_hcr$om
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M02"&q=="q0"&bound==30)[4,"file"]))
oms[["h9"]]=MSE_hcr$om

plot(FLStocks(llply(oms,window,start=2015,end=2044)))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.**  Operating Model runs for Multifan-CL scenario Alt1 with M=0.2; bound=30% and Btrhreshold=0.6 and FTarget=0.6.

```{r}
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M04"&q=="q0"&bound==30)[1,"file"]))
oms=FLStocks("h6"=MSE_hcr$om)
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M04"&q=="q0"&bound==30)[2,"file"]))
oms[["h7"]]=MSE_hcr$om
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M04"&q=="q0"&bound==30)[3,"file"]))
oms[["h8"]]=MSE_hcr$om
load(file.path(dirMedia,subset(key,mp==1&mfcl=="Base"&m=="M04"&q=="q0"&bound==30)[4,"file"]))
oms[["h9"]]=MSE_hcr$om

plot(FLStocks(llply(oms,window,start=2015,end=2044)))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.**  Operating Model runs for Multifan-CL scenario Alt1 with M=0.4; bound=30% and Btrhreshold=0.6 and FTarget=0.6.

```{r}
plot(FLStocks(llply(oms,function(x) window(iter(x,1),start=2015,end=2044))))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.**  Operating Model runs, single iter, for Multifan-CL scenario Alt1 with M=0.2; bound=30% and Btrhreshold=0.6 and FTarget=0.6.

```{r, eval=FALSE}

#load("/home/laurie/Desktop/MEGAsync/mse/albn/data/alb-240.RData")

dir=scan("/home/laurie/Desktop/tmp/inputs/dir.txt",what=as.character())
  
mfcl=mlply(dir, function(x){
  if (length(grep("Alt5",dir[1])>0))
  readMFCL(file.path("/home/laurie/Desktop/tmp/inputs",x,c("plot-08.par.rep","08.par")))
  else
  readMFCL(file.path("/home/laurie/Desktop/tmp/inputs",x,c("plot-07.par.rep","07.par")))})

om=FLStocks2FLStock(mfcl)

rm(mfcl)

dir[c(is.na(catch(om)[,"2010"]))]
```

```{r, eval=FALSE}
load("/home/laurie/Desktop/MEGAsync/mse/albn/data/key.RData")

badOM=seq(dim(om)[6])[is.na(c(catch(om)[,"2011"]))]

badKey=subset(key,om%in%badOM)

plot(iter(om,badOM))
```

# MFCL Runs
```{r om}
#load("/home/laurie/Desktop/MEGAsync/mse/albn/data/alb-240.RData")

dir=scan("/home/laurie/Desktop/tmp/inputs/dir.txt",what=as.character())
  
mfcl=mlply(dir, function(x){
  if (length(grep("Alt5",dir[1])>0))
  readMFCL(file.path("/home/laurie/Desktop/tmp/inputs",x,c("plot-08.par.rep","08.par")))
  else
  readMFCL(file.path("/home/laurie/Desktop/tmp/inputs",x,c("plot-07.par.rep","07.par")))})

om=FLStocks2FLStock(mfcl)

rm(mfcl)

dir[c(is.na(catch(om)[,"2010"]))]
```
# Agreed Validation Steps

##  Use the same random deviates across all scenarios for 100 iters



