---
title: "North Atlantic Albacore MSE"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---


```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               fig.width =10, 
               fig.height=8,
               fig.path  ="../tex/om-")
iFig=0
iTab=0
```

```{r init}
library(plyr)
library(dplyr)
library(stringr)
library(reshape2)
library(ggplot2)
library(ggplotFL)
library(FLCore)
library(FLBRP)

dirMy ="/home/laurie/Desktop/MEGAsync/mse/albn"
dirTex=file.path(dirMy,"tex")
dirDat=file.path(dirMy,"data")
dirInp=file.path(dirMy,"inputs")
```


```{r key}
runs=scan(file.path(dirInp,"om.txt"),what=as.character())
runs=mdply(runs,function(x)
     unlist(strsplit(gsub("bounded","",gsub(".RData","",x)),split="_")))[,c(4,5,6)]
runs=transmute(runs,om=as.numeric(gsub("om", "",V3)),
                    mp=as.numeric(gsub("hcr","",V4)),
                    bound=as.numeric(V5),
                    file =scan(file.path(dirInp,"om.txt"),what=as.character()))

key=read.csv(file.path(dirInp,"omKey.txt"),sep="")
key=ddply(key,.(om), with, unlist(strsplit(ac(id),split="_")))
names(key)=c("om","mfcl","m","steepness","q")

mp=data.frame(t(matrix(c(1,0.4,0.1,0.6,0.6,
                         2,0.4,0.1,0.6,0.7,
                         3,0.4,0.1,0.6,0.8,
                         4,0.4,0.1,0.6,0.9,
                         5,0.4,0.1,0.6,1.0,
                         6,0.4,0.1,0.8,0.6,
                         7,0.4,0.1,0.8,0.7,
                         8,0.4,0.1,0.8,0.8,
                         9,0.4,0.1,0.8,0.9,
                         10,0.4,0.1,0.8,1.0,
                         11,0.4,0.1,1.0,0.6,
                         12,0.4,0.1,1.0,0.7,
                         13,0.4,0.1,1.0,0.8,
                         14,0.4,0.1,1.0,0.9,
                         15,0.4,0.1,1.0,1.0),5,15)))
names(mp)=c("mp","blim","fmin","btrig","ftar")


key=merge(key,runs,by="om")
key=merge(key,mp,by="mp")
key=key[order(key$om),]

save(key,file=file.path(dirDat,"key.RData"))
```

```{r readSS, eval=FALSE}
getSS<-function(trial){
  
  err=try(load(trial))
  if ("try-error"%in%is(err)) {
    cat(trial,file="/home/laurie/Desktop/tmp/err.txt\n",append=TRUE)
    print(trial)
    return(NULL)}

  stk=MSE_hcr$om
 
  srr=fmle(as.FLSR(window(iter(stk,1),end=2013),model="bevholt"),control="silent")
  eql=FLBRP(window(iter(stk,1),end=2013),sr=srr)
  stk=window(stk,start=2014,end=2044)
  res=model.frame(FLQuants(stk,"ssb","fbar","catch"),drop=TRUE)
  ref=computeRefpts(eql)[c("msy","virgin"),c("ssb","harvest","yield"),drop=TRUE]
  
  mmm=transmute(res,year    =year,
                    stock   =ssb,
                    harvest =fbar,
                    catch   =catch,
                    msy     =ref["msy","yield"],
                    bmsy    =ref["msy","ssb"],
                    fmsy    =ref["msy","harvest"],
                    b0      =ref["virgin","ssb"])
  rm(MSE_hcr)
 
  mmm}

smryStats=ddply(key,.(file), with, getSS(file.path("/media/laurie/FREECOM HDD/nalbMse",file)))
save(smryStats,file=file.path(dirDat,"smryStats"),compress="xz")
```

```{r check-1, eval=FALSE}
load("/media/laurie/FREECOM HDD/nalbMse/MSE_hcr_om1_hcr1_bounded20.RData")
ggplot()+
     geom_line(aes(year,data),data=as.data.frame(MSE_hcr$tac[,ac(2015:2044),,,,56]),col="black")+
     geom_line(aes(year,data),data=as.data.frame(catch(MSE_hcr$om)[,ac(2015:2044),,,,56]),col="red")+
     geom_line(aes(year,data),data=as.data.frame(catch(MSE_hcr$mp)[,ac(2015:2040),,,,56]),col="green")

tac=MSE_hcr$tac
ctc=catch(MSE_hcr$om)[,dimnames(tac)$year]

plot(tac)+
 geom_line(aes(date,data,col=iter),data=as.data.frame(tac[,,,,,1:5]))
 
 refs=subset(na,year==2014&!duplicated(na$file))[,c("file","msy","bmsy","fmsy","b0")]
 refs=merge(refs,key)
 
 length(refs)
```

```{r ref-1}
library(GGally)

load(file.path(dirDat,"key.RData"))
load(file.path(dirDat,"smryStats.RData"))

refs=merge(subset(key,mp==1&bound==30),
           smryStats[!duplicated(smryStats$file),],by="file")

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_smooth(...,method="lm",se=FALSE)+
    geom_point(...)}

ggpairs(subset(refs,q=="q0")[,c("steepness","msy","bmsy","fmsy","b0")],
  mapping = ggplot2::aes(color=steepness),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(my_smooth,size=1,shape=21)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of reference points for the assumed values of scenarios.


```{r ref-2}
ggpairs(subset(refs,q=="q0")[,c("m","msy","bmsy","fmsy","b0")],
  mapping = ggplot2::aes(color=m),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(my_smooth,size=1,shape=21)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of reference points for assumed natural mortality.

```{r ref-3}
ggpairs(subset(refs,q=="q0")[,c("mfcl","msy","bmsy","fmsy","b0")],
  mapping = ggplot2::aes(color=mfcl),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(my_smooth,size=1,shape=21)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of reference points for the Multifan-CL scenarios.


```{r ref-4}
ggpairs(subset(refs,mfcl=="Base")[,c("q","msy","bmsy","fmsy","b0")],
  mapping = ggplot2::aes(color=q),
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower = list(continuous = wrap(my_smooth,size=1,shape=21)),
  #diag = list(continuous = wrap("densityDiag",alpha=.1)),
  diag=list(continuous=wrap(my_density,alpha=0.2)),
  title = "")+theme_bw(14)+
  theme(legend.position ="none", 
       panel.grid.major =element_blank(), 
       axis.ticks       =element_blank(), 
       axis.text.x      =element_blank(), 
       axis.text.y      =element_blank(),
       panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) 
```
**Figure `r iFig=iFig+1; iFig`.** Comparison of reference points for the Base Case contrasting hypothesis about trends in catchability.

