---
title: "ALB OEM"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r knitr, echo=FALSE}
library(knitr)

opts_chunk$set(comment=NA, 
               fig.width =8, 
               fig.height=5,
               fig.path  ="../tex/oem-",
               warning=FALSE, 
               message=FALSE, 
               error  =FALSE, 
               echo   =FALSE, 
               eval   =TRUE,
               cache  =TRUE)
iFig=0
```

```{r init, echo=FALSE}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(FLBRP)
library(ggplotFL)
library(diags)
library(mpb)

rodFn=FLife:::rodFn
```

#Biomass Dynamic

```{r biodyn-cpue}
data=read.csv("/home/laurie/ownCloud/ALBAss/ALBAss/Analysis/biodyn/indices/ALB_N_CPUE_MASTER_20160503_v2.csv")
cpue=FLQuants(dlply(data,.(fleet), with, as.FLQuant(data.frame(year=year,data=stdcpue))))

save(cpue,file="/home/laurie/Desktop/MEGAsync/mse/albn/data/cpue.RData")

plot(cpue[-4])+
  theme_bw()+theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.** Time series of CPUE indices used in biomass dynamic assessment model.

```{r}
library(mpb)

load("/home/laurie/Desktop/SCRS/ownCloud-2016/ALBAss/ALBAss/Analysis/biodyn/albn2016/data/TFGO.RData")
```


```{r biodyn-rsdl}
bd=bds2[[1]]
dgs=transform(bd@diags,fleet=name)

ggplot(subset(dgs,!is.na(residual)))+
  geom_abline(aes(slope=0,intercept=0))+
  geom_point(aes(year,residual),shape=21)+
  geom_smooth(aes(year,residual),se=FALSE)+
  facet_grid(.~fleet,scale="free",space="free")+
  xlab("Year")+ylab("Residuals")+
  theme_bw()+theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.**  Residuals from fit to CPUE by biomass dynamic assessment model. 


```{r biodyn-ar}
ggplot(aes(residual,residualLag), data=dgs)+
  geom_point()+
  geom_smooth(method="lm")+
  geom_abline(aes(slope=0,intercept=0))+
  facet_wrap(~fleet,scale="free")+
  xlab(expression(Residual[t]))+ylab(expression(Residual[t]))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Autocorrelation of residuals (lag 1) from fit to CPUE by biomass dynamic assessment model.


```{r biodyn-acf, fig.height=5}
ggplot(ddply(subset(dgs,!is.na(residual)),.(fleet), with,
             data.frame(lag  =0:10,
                        value=c(acf(residual,plot=F,lag.max=10)[[1]]))))+
  geom_abline(aes(slope=0,intercept=0))+
  geom_linerange(aes(x=lag,ymin=0,ymax=value))+
  facet_wrap(~fleet)+
  xlab("Lag")+ylab("ACF")+
  theme_bw()+theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`.** Autocorrelation of residuals from fit to CPUE by biomass dynamic assessment model.

```{r biodyn-2}
ggplot(aes(qqx,qqy), data=dgs)+
  geom_point()+
  geom_line(aes(qqx,qqHat))+
  facet_wrap(~fleet,scale="free")+
  xlab(expression(Quantile[expected]))+ylab(expression(Quantile[observed]))+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`.** Quantile Quantile plot of residuals from fit to CPUE by biomass dynamic assessment model

```{r new}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(FLCore)
library(FLBRP)
library(ggplotFL)
library(diags)
library(mpb)

load("/home/laurie/Desktop/SCRS/ownCloud-2016/ALBAss/ALBAss/Analysis/biodyn/albn2016/data/TFGO.RData")
load("/home/laurie/Desktop/MEGAsync/mse/albn/data/cpue.RData")

bd=new("biodyn")

for (i in slotNames(bds2[[1]])[-4])
  slot(bd,i)=slot(bds2[[1]],i)

bd@indices=cpue[-4]

bd=fit(bd)

bd@indices=FLQuants(llply(bd@indices,propagate, 10))
bd@catch=propagate(bd@catch,10)

bdi=fit(bd)

FLQuantJK<-FLQuant
jk=fit(bd,jackknife(cpue[-4]))

pjk=FLCore:::FLParJK(params(bdi), orig=params(bd))

setMethod("jackSummary", signature(object="FLParJK"),
  function(object,...) {
            
   nms <-names(dimnames(object))
   idx <-seq(length(nms))[nms != 'iter']
   n   <-dims(sim)$iter 
            
   mn  <-object
   u   <-sim
   mnU <-apply(u, idx, mean)   
            
   SS <-apply(sweep(u, idx, mnU,"-")^2, idx, sum)
            
   bias <- (n-1)*(mn-mnU)
   se   <- sqrt(((n-1)/n)*SS)
   
   cov  <-FLPar(cov(model.frame(u)[,dimnames(u)[[1]]])*(n-1)*(n-1)/n)
   
   return(FLPars(hat=mn, mean=mnU, se=se, bias=bias, cov=cov))})


jackSummary(params(bd))

# jacknife FLQuants
jk    =mcf(FLQuants(llply(cpue,jackknife)))
datYrs=laply(jk,function(x) aaply(x,2,function(x) !all(is.na(x))))

jk2=FLQuants(mlply(seq(length(cpue)), function(x,n=sum(datYrs)) 
         FLQuant(NA,dimnames=list(year=dimnames(datYrs)[[2]],iter=seq(n)))))
  
aaply(datYrs,1,sum)

    for (j in seq(length(cpue))[-i]){

      # get other indices dims right
      bigItUp=propagate(cpue[[j]],dim(cpue[[j]])[2])

      # create an FLQuant that can be JKed
      jk=combine(jk[[i]],bigItUp)
      }
```

**Figure `r iFig=iFig+1; iFig`.** 

```{r new-2}
library(plyr)

jk=mcf(FLQuants(llply(cpue,jackknife)))
jk=combine(jk[[1]],jk[[2]])

```

