---
title: "North Atlantic Albacore MSE"
subtitle: "Agreed Validation Steps Before Advice Will Be Given"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---
```{r, echo=FALSE, warning=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = FALSE)

opts_chunk$set(cache     =TRUE, 
               cache.path="cache/validation",
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               fig.width =8, 
               fig.height=4,
               fig.path  ="../tex/validation",
               cache.path="../cache/validation")
iFig=0
iTab=0
```

```{r data}
library(FLCore)
library(ggplotFL)
library(FLBRP)
library(mpb)
library(plyr)

dirMy  ="/home/laurence/Desktop/sea++/xval/manuscripts/peerReview/albn-mse"
dirInp =file.path(dirMy,"inputs")
dirMfcl=file.path(dirInp,"mfcl")
dirDat =file.path(dirMy,"data")
```

# Validation

# Operating Models

```{r OM}
load(file.path(dirDat,"omKey.RData"))
runs=expand.grid(run=seq(240),Recruits=c(1,2))
runs=cbind(runs,omKey[runs$run,])

load(file.path(dirDat,"oms.RData"))
load(file.path(dirDat,"eqls.RData"))
```

## Same random deviates 

Use same random deviates across all scenarios, and check stability of higher and lower percentiles within and across OM/MP scenarios. i.e. run for 1000 iters for selected OM/MP combinations

## Check SRR and Spawner v F curves

To check SRR run with high F’s and the dynamics are working the way they should, i.e contrast in the Spawning stock size and what it gives on recruitment

```{r OM-check1}
source('~/Desktop/flr/FLBRP/R/fwd-setup.R')

run1=subset(runs,Run=="Base"&Catchability=="q0"&Recruits==1)
om =oms[ run1$run]
eql=eqls[run1$run]

fn<-function(i){
    x=om[[i]]
    y=eql[[i]]
    
    f=FLQuants(mlply(data.frame(f=seq(0,c(FLBRP:::refpts(y)["crash","harvest"]),length.out=11)), 
                 function(f) FLQuant(f,dimnames=list(year=2012:2060))))
    names(f)=rep("f",11)
           
    z=fwdWindow(x,end=2060,y)
    z=fwd(z,control=f,sr=y)

    cbind(run=i,ldply(z, function(j) model.frame(FLQuants(j,"ssb","fbar","rec","catch"),drop=TRUE)))}

dat=mdply(seq(length(om)),fn)
dat=transform(dat,M=run1[run,"M"],Steepness=run1[run,"Steepness"],run=run1[dat$run,"run"])
```

```{r OM-check1-2}
source('~/Desktop/flr/FLBRP/R/plot-ggplot.R')

refpts=FLBRP:::refpts

dt2=ldply(eql, function(x) plot(x)$data)
dt2=transform(dt2,M=runs[as.numeric(.id),"M"],
              Steepness=runs[as.numeric(.id),"Steepness"],
              run=runs[as.numeric(.id),"run"])
```

```{r OM-check1-plot}
ggplot(subset(dat,year%in%seq(2040,2040,10)))+
  geom_line(aes(x,y,group=run),
            data=subset(dt2,pnl=="Equilibrium Recruitment v. SSB"))+
  geom_point(aes(ssb,rec,group=fbar,col=factor(fbar)),size=2)+
  facet_grid(M~Steepness)+
  theme(legend.position="none")+
  ylab("Recruits")+xlab("SSB")
```
**Figure `r iFig=iFig+1; iFig:

```{r OM-check1-plot2}
ggplot(subset(dat,year%in%seq(2040,2040,10)))+
  geom_line(aes(y,x,group=run),
            data=subset(dt2,pnl=="Equilibrium SSB v. F"))+
  geom_point(aes(ssb,fbar,group=fbar,col=factor(fbar)),size=2)+
  facet_grid(M~Steepness)+
  theme(legend.position="none")+
  ylab("F")+xlab("SSB")
```
**Figure `r iFig=iFig+1; iFig:

## Crosstest
*  Conduct a crosstest, i.e. run OM without feedback generate catch and CPUE fit SA, every 3 years and compare the OM and stock assessment (SA)

## OEM in crosstest

*  Use OEM in cross test

```{r OM-xtext}
library(mpb)

fn2<-function(i){
    x=om[[i]]
    y=eql[[i]]
    f=FLQuant(c(refpts(y)["msy","harvest"]),dimnames=list(year=2012:2060))
           
    z=fwdWindow(x,end=2060,y)
    z=fwd(z,f=f,sr=y)
    
    z}
    
prj=FLStocks(mlply(data.frame(i=seq(length(om))),fn2))    

fn3<-function(i,start,end,prj){
    
    print(paste(i,start,end))
  
    mp=as(window(prj[[i]],start=start,end=end),"biodyn")
    #mp@indices=FLQuants("1"=window((stock(prj[[i]])[,-1]+stock(prj[[1]])[,-dim(prj[[i]])[2]])/2,
    #                               start=start,end=end))
    mp@indices=FLQuants("1"=window(catch(prj[[i]])/fbar(prj[[1]]),start=start,end=end))
    
    mp=fwd(    mp,catch=catch(mp))
    setParams( mp)=mp@indices[[1]]
    setControl(mp)=params(mp)
    mp1=try(fit(mp))
  
    if (is(mp1)=="try-error") return(mp) else return(mp1)}

mps=mpb:::biodyns(mlply(expand.grid(i=seq(12),start=c(1930,1980),end=2011), fn3, prj=prj))
```

```{r OM-xtext-plot-b}
dat=ldply(mps, function(x) plot(FLQuants(x,"Biomass"=stock,
                                           "F"=function(x) catch(x)/stock(x)[,dimnames(catch(x))$year]))$data)

dat=cbind(expand.grid(i=seq(12),start=c(1930,1950,1970,1980),end=2011)[dat$.id,],dat)
dat=cbind(run1[dat$i,],dat)

plot(FLQuants(window(prj[[1]],end=2011),"Biomass"=stock))+
  geom_line(aes(year,data,col=factor(Steepness)),data=subset(dat,qname=="Biomass"))+
  facet_grid(start~M,scale="free_y")+
  xlab("Year")+ylab("Biomass")
```

**Figure `r iFig=iFig+1; iFig`** Crosstest comparision of biomass with MFCL estimates.


```{r OM-xtext-plot-f}
plot(FLQuants(window(prj[[1]],end=2011),"F"=function(x) catch(x)/stock(x)))+
  geom_line(aes(year,data,col=factor(Steepness)),data=subset(dat,qname=="F"))+
  facet_grid(start~M,scale="free_y")+
  xlab("Year")+ylab("Harvest Rate")
```

**Figure `r iFig=iFig+1; iFig`** Crosstest comparision of harvest rate with MFCL estimates.

```{r OM-xtext-saa}
load(file.path(dirDat,"saa.RData"))
load(file.path(dirDat,"TFGO.RData"))

saa=saa[do.call("order",saa[,c(1:2,4)]),]
sel=dlply(subset(saa,qname%in%unique(saa$qname)[c(1,7,10,12,12)]&X1%in%run1$run),.(X1),function(x) 
  FLQuants(dlply(x,.(qname), with, as.FLQuant(data.frame(data=data,age=as.numeric(age))))))

yrRng=ddply(diags(bds2[[1]]),.(name), with, range(year))
names(yrRng)=c("name","minyear","maxyear")
yrRng=data.frame(yrRng,sel=names(sel[[1]])[c(3,1,2,4,4)])
yrRng[c(1:2,4:5),"maxyear"]=2040
yrRng[3,         "maxyear"]=2012

albOem<-function(i,j,year,timing=0.5,om=NULL){
  window(apply(oem(om,setPlusGroup(sel[[i]][[min(j,4)]],range(om)["plusgroup"]),timing=timing),2,sum),
         start=yrRng[j,"minyear"],end=min(yrRng[j,"maxyear"],year))}

fn4<-function(i,start,year){
  
  print(paste(i,start,year))
  
  mp=as(window(prj[[i]],start=start,end=year),"biodyn")
  mp@indices=FLQuants(mlply(expand.grid(i=i,j=1:5,year=year),albOem, timing=0.5, om=prj[[i]]))
  mp=fwd(    mp,catch=catch(mp))
  
  setParams( mp)=mp@indices
  params(mp)["r"]=0.3
  setControl(mp)=params(mp)
  control(mp)[substr(dimnames(control(mp))$params,1,1)=="q",1]=1
  mp1=try(fit(mp))

  mp1}

mpsaa=mlply(expand.grid(i=seq(12),start=c(1930,1950,1980),year=2011),fn4)
```

```{r}
save(mpsaa,file="/home/laurence/Desktop/tmp/mpsaa.RData")
```

```{r OM-xtext-saa-plot-b}
dat=ldply(mpsaa, function(x){
  
           if ("try-error" %in% is(x)) return(NULL)
  
           plot(FLQuants(x,"Biomass"=stock,
                           "F"      =function(x)
                                       catch(x)/stock(x)[,dimnames(catch(x))$year]))$data})
dat=cbind(dat,run1[dat$i,])

dt2=ldply(prj, function(x) plot(FLQuants(window(x,end=2011),"Biomass"=stock))$data)
dt2=cbind(dt2,run1[dt2$i,])

ggplot()+
  geom_line(aes(year,data),                  data=subset(dt2,qname=="Biomass"))+
  geom_line(aes(year,data,col=factor(start)),data=subset(dat,qname=="Biomass"))+
  facet_grid(Steepness~M,scale="free_y")+
  xlab("Year")+ylab("Biomass")
```

**Figure `r iFig=iFig+1; iFig`** Crosstest comparision of biomass with MFCL estimates.


```{r OM-xtext-saa-plot-f}
dt2=ldply(prj, function(x) plot(FLQuants(window(x,end=2011),"F"=function(x) catch(x)/stock(x)))$data)
dt2=cbind(dt2,run1[dt2$i,])

ggplot()+
  geom_line(aes(year,data),                  data=subset(dt2,qname=="F"))+
  geom_line(aes(year,data,col=factor(start)),data=subset(dat,qname=="F"))+
  facet_grid(Steepness~M,scale="free_y")+
  xlab("Year")+ylab("Harvest Rate")
```

**Figure `r iFig=iFig+1; iFig`** Crosstest comparision of harvest rate with MFCL estimates.

```{r}
save(par,run1,file="/home/laurence/Desktop/tmp/dat.RData")
```

```{r OM-xtext-saa-hist-f,eval=FALSE}
ggplot(cbind(par,run1[par$i,]))+
  geom_histogram(aes(r))+
  facet_grid(.~M)
```
**Figure `r iFig=iFig+1; iFig`** Estimates of r.


```{r OM-xtext-saa-hist-k,eval=FALSE}
ggplot(cbind(par,run1[par$i,]))+
  geom_histogram(aes(k))+
  facet_grid(.~M)
```
**Figure `r iFig=iFig+1; iFig`** Estiamtes of K.

```{r OM-gorka,eval=FALSE}
msePar=ddply(key,.(file), with, {
    load(file.path("/media/laurence/FREECOM HDD/nalbMse",file))
    model.frame(params(MSE_hcr[["mp"]])[c("r","k")])
    })
```
**Figure `r iFig=iFig+1; iFig`** Estiamtes of r.

## F=$F_{MSY}$
*  For all OM/MP trials run simple F=Ftarget projection, to check dynamics

### OM with feedback
*  Run OM with feedback for an F target of FMSY  and compare to F projection

### OM with feedback and $B_{MSY}$ as $B_{Thresh}$
*  Run a OM with feedback for an F target of FMSY and an Btreshold of BMSY, compare to above.

### OM with feedback and $B_{MSY}$ as $B_{Thresh}$ and TAC Bounds 
*  Run a OM with feedback for an F target of FMSY and an Btreshold of BMSY plus TAC bounds of 20, 25 and 30%, compare to above.

### Factorial Design

*  Run scenarios using a factorial design, i.e. main effects, 1st, 2nd, ... order interactions, see if you can predict the performance indicators

## Refpts
*  Compare OM and MP reference points

## TAC
*  Check TAC output by MP and Catch taken from OM, iteration by iteration.

## Conditioning
*  OM conditioning, of historic and future, i.e. calculate the OM production functions and compare trajectories to these.

## Refpts
*  Compare OM reference points and statistics such as K, r, … to MP values

## Check SA
*  Check SA, e.g. hitting bounds, convergence

## TAC
*  Compare TAC output from MP compared to Catch from OM




