---
title: "Crossvalidation I"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

Estimate and compare four different forms of error i.e.

+ Model errors: from model fits
+ Prediction errors: based on leave-one-out jackknife procedure
+ Hindcast: Retrospective with projection and then compare predictions with observations
+ One-step: Retrospective with leave-one-out for final year 

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
dirMy="/home/laurence/Desktop/sea++/xval"
dirDat=file.path(dirMy,"data")
dirVpa=file.path(dirMy,"inputs/vpa")
dirTex=file.path(dirMy,"tex")
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               fig.width =10, 
               fig.height=8,
               fig.path  ="../tex/xval1-")

iFig=0
iTab=0
```

```{r init}
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(ggplotFL)
library(FLCore)
library(diags)
library(stringr)
```

```{r data}
m=c(0.3800,0.3000,0.2400,0.2000,0.1800,0.1600,0.1400,0.1300,0.1200,0.1000)

vpa=FLStocks("boot"=readVPA2Box(file.path(dirVpa,"ebft/bfte2017.c1"),m=m))
```

```{r vpa}
plot(vpa[["boot"]])
```
**Figure x.`r fig=1; fig`**  VPA

# Model residuals
```{r source}
source('~/Desktop/flr/diags/R/read-VPA2Box-FLIndices.R', echo=TRUE)
source('~/Desktop/flr/diags/R/io.VPA2BoxV2.R', echo=TRUE)
source(file.path(dirMy,'R/jackknife-vpa2box.R'))
```

```{r me}
vpa[["fit"]]=run.vpa2box(file.path(dirVpa,"ebft/sims/bfte2017.c1"),m=m)

dgs=cbind(error="model",iter=0,diags.vpa2box(file.path(dirVpa,"ebft/sims/MINUS0.R")))
```

# Prediction residuals 

```{r jack,eval=FALSE}
press=jackknife.vpa2box(file.path(dirVpa,"ebft/sims/bfte2017.c1"),m=m)

save(press,file=file.path(dirDat,"press.RData"),compress="xz")
```

Returns a list with `FLStocks` and a `data.frame`, the `FLStocks` contains in the first element the fit to all the data and in the second element an FLStock with `iters` for each deleted CPUE observation. The `data.frame` contains the predicted CPUE values from each iteration of the jackknife.


```{r press, eval=FALSE}
load(file.path(dirDat,"press.RData"))

idx=readVPA2BoxIndices(file.path(dirVpa,"ebft/sims/bfte2017.d1"))
xv =predError(idx,press[[1]][[2]],press[[2]])

ggplot()+
  geom_point(aes(as.integer(ac(year)),p.error),col="red",data=xv)+
  geom_point(aes(year,residual),data=as.data.frame(dgs))+
  facet_wrap(~name,ncol=3)

ddply(xv, .(name),with,var(p.error )^0.5)[,2]/
ddply(dgs,.(name),with,var(residual)^0.5)[,2]

ggplot(xv)+geom_boxplot(aes(name,p.error))
ggplot(dgs)+geom_boxplot(aes(name,residual))

```