---
title: "Exploratory Data Analysis" 
subtitle: "Eastern Bluefin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r dir, echo=FALSE}
dirMy="/home/laurence/Desktop/sea++/xval"
dirDat=file.path(dirMy,"data")
dirVpa=file.path(dirMy,"inputs/vpa")
dirTex=file.path(dirMy,"tex")
```

```{r knitr, echo=FALSE}
library(knitr)

opts_chunk$set(comment=NA, 
               fig.width =5.5, 
               fig.height=6,
               fig.path  ="../tex/vpaData-",
               warning=FALSE, 
               message=FALSE, 
               error  =FALSE, 
               echo   =FALSE, 
               eval   =TRUE,
               cache  =TRUE,
               cache.path="cache/vpaData")
iFig=0
iTab=0
```


```{r init}
library(ggplot2)
library(reshape2)
library(readxl)

library(plyr)
library(dplyr)

library(gam)

library(GGally)
library(corrplot)

#install.packages("FLCore", repos = "http://cloud.r-project.org/")

library(FLCore)

#source('~/Desktop/flr/diags/R/read-VPA2Box-FLIndices.R')

theme_set(theme_bw(14))
options(digits=3)

u=diags:::readVP2BoxIndices(file.path(dirVpa,"ebft/bfte2017.d1"))
names(u)=c("ESPMarTrap","MarPorTrap","JLL EastMed","JP LL NEA1","JP LL NEA2",
           "SP BB1",    "SP BB2",    "FR Aerial1",    "FR Aerial2",     "larval survey")

rng=ldply(u,function(x) range(x))
cv =ldply(u,function(x) as.data.frame(index.var(x),drop=TRUE))
obs=ldply(u,function(x) as.data.frame(index(    x),drop=TRUE))
obs=data.frame(obs[,1:2],obs=obs[,3],se=cv[,3])
obs=transform(obs,p0.025=qlnorm(0.025,log(obs),se),
                  p0.975=qlnorm(0.975,log(obs),se))

names(rng)[1]="name"

u=FLQuants(llply(u, index))
```

```{r raw}
ggplot(obs)+
  geom_line(aes(year,obs))+
  geom_point(aes(year,obs),size=.25)+
  geom_errorbar(aes(year,ymin=p0.025,ymax=p0.975),size=0.5)+
  #geom_ribbon(aes(year,ymin=p0.025,ymax=p0.975),alpha=0.05,col="blue")+
  facet_grid(.id~.,scale="free")+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** Time series of CPUE indices with 95% confidence intervals.


```{r}
scale<-function(x,y,...){
  args=list(...)
  
  if (length(args)==0) group=rep(1,length(x)) else group=args[[1]]  
  
  gm=gam(y~lo(x)+group,data=data.frame(x=x,y=y,group=group))

  res=data.frame(hat =predict(gm),
                 y     =gm$y,
                 x     =x,
                 group =group,
                 scl   =c(0,coefficients(gm)[-(1:2)])[as.numeric(as.factor(group))]
                 )
  res$y  =res$y  -res$scl
  res$hat=res$hat-res$scl
  
  if (length(args)==1) names(res)[4]=names(args)[1]  
  
  res[,-5]}

my_density <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_density(...,lwd=1)}

my_bar <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_bar(...)}

my_smooth <- function(data,mapping,...){
  ggplot(data=data,mapping=mapping)+
    geom_point(...,size=.5)+
    geom_smooth(...,method="lm",se=FALSE)}

my_ccf<-function(cpue,n=10){
cc=mdply(expand.grid(a=names(cpue),b=names(cpue)),
         function(a,b){
           #print(paste(a,b))
           res=model.frame(mcf(FLQuants(cpue[c(a,b)])))
           res=subset(res,!is.na(res[,7])&!is.na(res[,8]))

           if (dim(res)[1]>n){
             res=data.frame(lag=-n:n,data=ccf(res[,7],res[,8],plot=F,
                                                lag.max=n)$acf)
             return(res)}else{return(NULL)}}
           )}
```

```{r plot, fig.height=10,fig.width=8}
library(diags)

dat=subset(ldply(u,as.data.frame),!is.na(data)&!is.na(.id))
dat=ddply(dat,.(.id), with, data.frame(year=year,y=diags:::stdz(data)))

dat=with(dat,scale(x=year,y=y,name=.id))

ggplot(dat)+
  geom_line( aes(x,hat),data=dat[,c("x","y","hat")],col="grey60")+
  geom_line( aes(x,hat))+
  geom_line( aes(x,y))+
  geom_point(aes(x,y))+
  facet_grid(name~.,scale="free",space="free_x")+
  theme_bw(14)+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; iFig`.** Time series of CPUE indices, continuous black line is a lowess smother showing the average trend by area (i.e. fitted to year for each area with series as a factor)

```{r plot2, fig.height=10,fig.width=8}
ggplot(transform(dat,residual=y-hat))+
  geom_hline(aes(yintercept=0))+
  geom_point(aes(x,residual),position=position_dodge(width = 1))+
  geom_line(aes(x,residual),alpha=0.5)+
  geom_linerange(aes(x,ymin=0,ymax=residual),position=position_dodge(width = 1))+
  theme(legend.position="bottom")+
  facet_grid(name~.,scale="free",space="free_x")+
  theme_bw(14)+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1; iFig`.** Time series of residuals from the lowess fit.


```{r plot-pairs-n, fig.height=8,fig.width=8}
dat=subset(ldply(u,as.data.frame),!is.na(data)&!is.na(.id))
dat=ddply(dat,.(.id), with, data.frame(year=year,y=diags:::stdz(data)))

mat=dcast(dat,year~.id,value="y")
names(mat)=gsub(" ", "_",names(mat))

ggpairs(mat[,-1],
  upper=list(continuous=wrap("cor",size=4, hjust=0.5)),
  lower=list(continuous = wrap(my_smooth)),
  diag=list(continuous="bar"))
```
**Figure `r iFig=iFig+1; iFig`.** Pairwise scatter plots to look at correlations between Indices, North.

```{r plot-cor-n, fig.height=8,fig.width=8}
cr=cor(mat[,-1],use="pairwise.complete.obs")
dimnames(cr)=list(gsub("_"," ",names(mat)[-1]),gsub("_"," ",names(mat)[-1]))
cr[is.na(cr)]=0
corrplot(cr,diag=F,order="hclust",addrect=3)  +          
             theme(legend.position="bottom")  
```
**Figure `r iFig=iFig+1; iFig`.** Plot of the correlation matrix for the Southern CPUE indices, blue indicate a positive correlation  and red negative. the order of the indices and the rectanglur boxes are chosen based on a hierarchical cluster analysis using a set of dissimilarities for the indices being clustered.

```{r ccf-n, fig.height=8,fig.width=8}
is(u
   )
#cc=my_ccf(u,n=7)

#ggplot(cc)+
#  geom_linerange(aes(x=lag,ymin=0,ymax=data))+
#  facet_grid(a~b)+
#  geom_vline(aes(xintercept=0))+
#  theme_bw(14)    
```
**Figure `r iFig=iFig+1; iFig`** Cross correlations between Northern indices, to identify potential lags due to year-class effects.


```{r ccf-n3, fig.height=8,fig.width=8}
waa=read.table(file.path(dirVpa,"ebft/bfte2017.d1"),skip=427,nrows=483-427)
waa=waa[waa[,1]%in%c(6,7,10),]
names(waa)[c(1:2)]=c("name","year")
waa=melt(waa,id=c("name","year"))
waa=transmute(waa,name=name,year=year,age=as.numeric(variable),wt=value)
waa$name=rng[waa$name,1]

paa=read.table(file.path(dirVpa,"ebft/bfte2017.d1"),skip=264,nrows=422-264)
names(paa)[1:2]=c("name","year")
paa=melt(paa,id=c("name","year"))
paa=transmute(paa,name=name,year=year,age=as.numeric(variable),p=value)
paa$name=rng[paa$name,1]

paa=merge(paa,waa,by=c("name","year","age"),all.x=TRUE)
paa=transform(paa,decade=10*(year%/%10))

nms=unique(waa$name)

raa=ddply(subset(paa,!(name%in%nms)),.(name,decade), transform, p=p/sum(p))
baa=subset(subset(paa, (name%in%nms)))
baa=ddply(subset(baa,!(is.na(baa$wt))),.(name,decade), transform, p=wt*p/sum(wt*p))
```

```{r ccf-n4, fig.height=8,fig.width=8}
nm.=c(nms,"FR Aerial1","FR Aerial2")

ggplot(raa)+
  geom_histogram(aes(age,weight=p),bin=1)+
  geom_vline(aes(xintercept=min-0.25),data=subset(rng,!(name%in%nm.))[-(8:9),],col="darkgreen")+
  geom_vline(aes(xintercept=max+0.25),data=subset(rng,!(name%in%nm.))[-(8:9),],col="darkgreen")+
  facet_grid(decade~name,scale="free_y",space="free")+
  theme_bw()+xlab("Year")+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1; iFig`** Catch compostion, vertical lines show the ages used in calibration.

```{r ccf-n5, fig.height=8,fig.width=8}
ggplot(baa)+
  geom_histogram(aes(age,weight=p),bin=1)+
  geom_vline(aes(xintercept=min-0.25),data=subset(rng,(name%in%nms))[-(8:9),],col="darkgreen")+
  geom_vline(aes(xintercept=max+0.25),data=subset(rng,(name%in%nms))[-(8:9),],col="darkgreen")+
  facet_grid(decade~name,scale="free_y",space="free")+
  theme_bw()+xlab("Year")+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1; iFig`** Catch biomass compostion, vertical lines show the ages used in calibration.

```{r ccf-n2, fig.height=8,fig.width=8}
paa=read.table(file.path(dirVpa,"ebft/bfte2017.d1"),skip=264,nrows=422-264)
names(paa)[1:2]=c("name","year")
paa=melt(paa,id=c("name","year"))
paa=transform(paa,age=as.numeric(variable),n=value)

paa$n[paa$n==0]=.1
paa=subset(paa,name<8)
paa$name=rng[paa$name,1]
#cca=ddply(paa,.(name,year), with, FLife:::cc(age,n))
ccFn<-function (age, n) 
{
  lm = lm(log(n) ~ age)
  hat = exp(predict(lm))
  sel = (n/hat)/max(n/hat)
  data.frame(age = age, obs = n, hat = hat, sel = sel)
}
cca=ddply(paa,.(name,year), with, ccFn(age,n))

ggplot(cca)+
  geom_line(aes(age,sel,group=year),col="grey")+
  geom_point(aes(age,sel,col=factor(5*(year%/%5))),size=.25)+
  geom_smooth(aes(age,sel),se=FALSE)+
  geom_vline(aes(xintercept=min-0.25),data=rng[-(8:9),],col="darkgreen")+
  geom_vline(aes(xintercept=max+0.25),data=rng[-(8:9),],col="darkgreen")+
  facet_wrap(~name,ncol=2)+
  theme_bw()+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1; iFig`** Catch curve analyses, vertical lines show the ages used in calibration.

```{r cca}
caa=read.table(file.path(dirVpa,"ebft/bfte2017.d1"),skip=23,nrows=71-23)
names(caa)[1]="year"
caa=transform(melt(caa,id="year"),age=as.numeric(variable))
caa=transform(ddply(subset(caa,age<10&value!=0),.(year), with, FLife:::cc(age,value)),decade=10*(year%/%10))

ggplot(caa)+
  geom_line(aes(age,sel,group=year),col="grey")+
  geom_point(aes(age,sel,col=factor(5*(year%/%5))),size=.25)+
  geom_smooth(aes(age,sel),se=FALSE)+
  facet_wrap(~decade,ncol=2)+
  theme_bw()+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1; iFig`** Selection pattern of the entire catch-at-age.

```{r sel, fig.height=4, eval=FALSE}
dat=cbind(subset(caa,age==9)[,c("year","sel")],pg=ddply(subset(caa,age>9),.(year),with,mean(sel))[,"V1"])
dat=transform(dat,fratio=pg/sel)

ggplot(melt(dat[,-4],id="year"),aes(year,value,col=variable))+
  geom_point()+
  geom_smooth(se=FALSE)+
   theme_bw()+theme(legend.position="bottom")+
  xlab("Year")+ylab("Selection Pattern")+
  scale_colour_manual(values=c("#999999", "#E69F00"), 
                       name="Selection \n Pattern",
                       breaks=c("sel", "pg"),
                       labels=c("Age 9", "Plus Group"))

#**Figure `r iFig=iFig+1; iFig`** Plus group and age 9 selection patterns.
```

```{r pg,fig.height=4, eval=FALSE}
vpa=readVPA2Box("/home/laurie/Desktop/kobe/inputs/bfte/2014/vpa/reported/med/bfte2014.c1")

vp=as.data.frame(harvest(vpa)[10,,,,,1]/harvest(vpa)[9,,,,,1],drop=TRUE)

ggplot(melt(dat[,-(2:3)],id="year"),aes(year,value))+
  geom_point()+
  geom_line(aes(year,data),data=vp,col="red")+
  geom_smooth(se=FALSE)+
  scale_colour_brewer(palette = "Set1")+
  theme_bw()+
  xlab("Year")+ylab("F Ratio")

#**Figure `r iFig=iFig+1; iFig`** Plus group
```
