---
title: "Jackknife"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               fig.width =10, 
               fig.height=8,
               fig.path  ="../tex/jk-")

iFig=0
iTab=0
```

```{r init}
library(plyr)
library(dplyr)
library(stringr)
library(reshape2)
library(ggplot2)
library(ggplotFL)
library(FLCore)
library(FLBRP)
library(FLife)
library(scales)
library(popbio)
library(diags)
library(stringr)

dirMy="/home/laurence/Desktop/SCRS/bftAss/bft2017"
dirDat=file.path(dirMy,"data")
dirInp=file.path(dirMy,"inputs/2017/VPA")
dirTex=file.path(dirMy,"tex")

source('~/Desktop/flr/FLife/R/refs.R')

m=c(0.3800,0.3000,0.2400,0.2000,0.1800,0.1600,0.1400,0.1300,0.1200,0.1000)

base=readVPA2Box(file.path(dirInp,"base/bfte2017.c1"),m=m)
```

```{r jack,eval=FALSE}
source('~/Desktop/flr/mpb/R/jackknife-vpa2box.R')

jk=mlply(file.path(dirInp,"base/bfte2017.c1"),jackknife.vpa2box,m=m)

save(jk,file=file.path(dirDat,"jk.RData"),compress="xz")
```



```{r refs}
source('~/Desktop/flr/FLife/R/refs.R')
source('~/Desktop/flr/FLife/R/lhPar.R')

dgs=mdply(data.frame(scen=file.path(dirInp,"base/MINUS0.R"),
                     stringsAsFactors=FALSE),
                     function(scen) diags.vpa2box(scen))
dgs=transform(dgs,Scenario=factor(scen,labels=c("Inflated")))
load(file.path(dirDat,"jk.RData"))

rfDat=ldply(jk, function(x) model.frame(refs(x[[1]][[2]], s=0.9)))
rfDat=cbind(dgs,rfDat)
save(rfDat,file=file.path(dirDat,"rfDat.RData"),compress="xz")
```


```{r ref2}
library(FLife)

source('~/Desktop/flr/FLife/R/refs.R')
mf2FLPar=FLife:::mf2FLPar

load(file.path(dirDat,"jk.RData"))

rfDatHat=ldply(jk, function(x) model.frame(refs(x[[1]][[1]], s=0.9)))
```


```{r ref3, eval=FALSE}
source('~/Desktop/flr/FLife/R/refs.R')
source('~/Desktop/flr/FLife/R/lhPar.R')
source('~/Desktop/flr/mpb/R/biodyn-jackSummary.R')

setMethod("jackSummary", signature(object="FLPar",sim="FLPar"),
          function(object,sim,...) {
            
            nms <-names(dimnames(object))
            idx <-seq(length(nms))[nms != 'iter']
            n   <-dims(sim)$iter 
            
            mn  <-object
            u   <-sim
            mnU <-apply(u, idx, mean)   
            
            SS <-apply(sweep(u, idx, mnU,"-")^2, idx, sum)
            
            bias <- (n-1)*(mn-mnU)
            se   <- sqrt(((n-1)/n)*SS)
            
            cov  <-FLPar(cov(model.frame(u)[,dimnames(u)[[1]]])*(n-1)*(n-1)/n)
            cor  =FLPar(cor(cov[drop=T]))
            
            return(FLPars("hat"=mn, "mean"=mnU, "se"=se, "cv"=se%/%mnU,
                          "bias"=bias, "biasRel"=bias%/%mnU,
                          "cov"=cov))})

load(file.path(dirDat,"jk.RData"))

rfs=llply(jk, function(x){
  
       res=FLPars(llply(x, refs, s=0.9))

       rf1=as(transmute(model.frame(res[[1]]),
                             ssmsy=s.current/s.f0.1_,
                             ffmsy=f.current/f.f0.1_,
                             r    =r,
                             rt   =rt),"FLPar")
       rf2=as(transmute(model.frame(res[[2]]),
                             ssmsy=s.current/s.f0.1_,
                             ffmsy=f.current/f.f0.1_,
                             r    =r,
                             rt   =rt),"FLPar")
       
       attributes(rf1)$iter.key=attributes(x[[1]])$iter.key
       jackSummary(rf1,rf2)})
       
save(rfs,  file="/home/laurie/Desktop/tmp/rfs.RData",  compress="xz")
```


```{r dat,fig.height=8,fig.width=6}
library(gam)
nms=unique(dgs$name)[c(1:4,6,5,7)]

save(dgs,file="/home/laurie/Desktop/tmp/dgs.RData",compress="xz")

scale<-function(x,y,...){
  args=list(...)
  
  if (length(args)==0) group=rep(1,length(x)) else group=args[[1]]  
  
  gm=gam(y~lo(x)+group,data=data.frame(x=x,y=y,group=group))

  res=data.frame(hat =predict(gm),
                 y     =gm$y,
                 x     =x,
                 group =group,
                 scl   =c(0,coefficients(gm)[-(1:2)])[as.numeric(as.factor(group))]
                 )
  res$y  =res$y  -res$scl
  res$hat=res$hat-res$scl
  
  if (length(args)==1) names(res)[4]=names(args)[1]  
  
  res[,-5]}

dat=with(subset(dgs,scen==dgs$scen[1]),scale(year,x,name=as.character(name)))


ggplot(dat)+
  geom_line( aes(x,hat),data=dat[,c("x","hat")],col="grey60")+
  geom_line( aes(x,hat))+
  geom_line( aes(x,y))+
  geom_point(aes(x,y,fill=name),shape=21)+
  scale_fill_brewer(palette = "Set1")+
  scale_y_continuous(breaks=c(-2,0,2))+
  facet_grid(name~.)+
  theme_bw(14)+xlab("Year")+ylab("CPUE")+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1; iFig`.** Time series of CPUE indices, continuous black line is a loess smother showing the average trend by area (i.e. fitted to year for each area with series as a factor)


```{r,fig.width=7,fig.height=7}
source('~/Desktop/flr/FLife/R/lhPar.R')

ggplot(aes(x,y,fill=Scenario,col=Scenario),data=dgs) +   
      geom_point(shape=21,size=2)+
      geom_smooth(se=FALSE,method="lm")+
      geom_abline(aes(slope=1,intercept=0))+
      xlab("Assessment Estimate")+ylab("Observered CPUE")+
      facet_wrap(~name,scale="free")+
      scale_fill_brewer(palette = "Set1")+
      scale_colour_brewer(palette = "Set1")+
      theme_bw()+
      theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Observed CPUE verses fitted, blue line is a linear regression fitted to points, black the y=x line. 

```{r,fig.width=7,fig.height=9}
dat=ddply(dgs, .(name), transform, residual=diags:::stdz(residual,na.rm=T))

ggplot(aes(year,residual,col=Scenario,fill=Scenario),data=dat) +
  geom_hline(aes(yintercept=0))      +
  geom_point(shape=21,size=2)                       +
  #geom_linerange(aes(year,ymin=0,ymax=residual),position="jitter")                       +
  stat_smooth(method="loess",se=FALSE,fill="blue", alpha=0.1)  +
  facet_wrap(~name,scale="free",ncol=2)+
  scale_fill_brewer(  palette="Set1")+
  scale_colour_brewer(palette="Set1")+
  theme_bw()+ylab("Residual")+xlab("Year")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Plot of residuals by year, lines are loess smoothers.

```{r,fig.width=7,fig.height=7}
ggplot(dgs)                                              +
  geom_point( aes(residual,residualLag,col=Scenario,fill=Scenario),shape=21)                  +
  stat_smooth(aes(residual,residualLag,col=Scenario,fill=Scenario)
              ,method="lm",se=FALSE,fill="blue", alpha=0.1)      +
  geom_hline(aes(yintercept=0))                           +
  facet_wrap(~name,scale="free",ncol=3)                   +
  xlab(expression(Residual[t])) + 
  ylab(expression(Residual[t+1]))+
  scale_fill_brewer(  palette="Set1")+
  scale_colour_brewer(palette="Set1")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Plot of autocorrelation, i.e. $residual_{t+1}$ verses $residual_{t}$, line is a linear regression through points.

```{r,fig.width=6,fig.height=6}
ggplot(dgs)                                           +
  geom_point( aes(qqx,qqy,  col=Scenario,fill=Scenario),size=2,shape=21)                            +
  stat_smooth(aes(qqx,qqHat,col=Scenario,fill=Scenario),
              method="lm",se=FALSE,fill="blue", alpha=0.1)         +
  facet_wrap(~name)+
  scale_fill_brewer(  palette="Set1")+
  scale_colour_brewer(palette="Set1")+
  theme_bw()+
  theme(legend.position="bottom")          
```

**Figure `r iFig=iFig+1;iFig`.** Quantile-quantile plot to compare residual distribution with the normal distribution, line is a linear regression.


```{r,fig.width=6,fig.height=8}
ggplot(aes(yhat, residual,col=Scenario,fill=Scenario),data=dgs)   +
  geom_hline(aes(yintercept=0))         +
  geom_point(shape=21)                          +
  stat_smooth(method="loess",se=FALSE,span=.9,fill="blue", alpha=0.1)   +
  facet_wrap(~name,scale="free",ncol=2)+
  scale_fill_brewer(  palette="Set1")+
  scale_fill_brewer(palette="Set1")+
  scale_colour_brewer(palette="Set1")+
  theme_bw()+
  theme(legend.position="bottom") 
```

**Figure `r iFig=iFig+1;iFig`.** Plot of residuals against fitted value, to check variance relationship, lines are loess smoothers.

```{r lm1,fig.height=5,fig.height=8}
library(GGally)

dat=ddply(transform(dgs,Scenario=factor(scen,labels=c("Reported","Inflated"))),
          .(Scenario,name), function(x)
            data.frame(year=x$year,x=x$x,cooksd=cooks.distance(lm(x$y~x$x-1))))

ggplot(dat)+
  geom_point(aes(x,cooksd,fill=name),shape=21,size=4)+
  scale_colour_brewer(palette = "Set1")+
  facet_grid(name~Scenario,scale="free",space="free")+
  theme_bw(16)+xlab("CPUE")+ylab("Cooks Distance")+
  theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`** Summary plots of Cooks Distance for the CPUE series fitted to the two VPA Scenarios.

```{r lm3,fig.height=5,fig.height=10}
ggplot(dat)+
  geom_point(aes(year,cooksd,fill=name),shape=21,size=4)+
  scale_colour_brewer(palette = "Set1")+
  facet_grid(name~Scenario,scale="free",space="free")+
  theme_bw(16)+xlab("Year")+ylab("Cooks Distance")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`** Summary plots of Cooks Distance for the CPUE series by year fitted to the two VPA Scenarios.

```{r lm,fig.height=8,fig.height=9}
dat=transform(dgs,Scenario=factor(scen,labels=c("Reported","Inflated")))
mdl=lm(log(y)~name*Scenario*x,data=dat)
p=ggnostic(mdl,mapping=ggplot2::aes(color=name))+
#  scale_colour_brewer(palette = "Set1")+
  theme_bw()+
  theme(legend.position="bottom")
```
<!-- **Figure iFig=iFig+1;iFig.** Summary plots of residuals, sigma, CVs and Cooks Distance for the CPUE series fitted to the two VPA Scenarios. -->

```{r lm2,fig.height=8,fig.width=8}
ggplot(ggnostic(mdl)$data)+
  geom_point(aes(.hat,.resid,size=.cooksd,col=Scenario))+
  scale_colour_brewer(palette = "Set1")+
  facet_wrap(~name)+
  theme_bw()+
  theme(legend.position="bottom")+
  xlab("Hat Values")+ylab("Studentized Residual")
```
**Figure `r iFig=iFig+1;iFig`.** Influence plots plotting residuals against hat values (i.e. leverage), size of bubble show the Cooks distance (i.e. the leverage).

```{r stats}
load("/home/laurie/Desktop/tmp/dgs.RData")
load("/home/laurie/Desktop/tmp/rfs.RData")
load("/home/laurie/Desktop/tmp/jks.RData")
load("/home/laurie/Desktop/tmp/rfDat.RData")
```

```{r influence_s, fig.height=8, fig.width=8}
dat=transform(rfDat,
              fmsy=f.current/f.f0.1,
              Scenario=factor(scen,labels=c("Inflated","Reported")))[,
                                    c("Scenario","name","year","fmsy")]
hat=transform(rfDatHat,
              hat=f.current/f.f0.1,
              Scenario=factor(X1,labels=c("Reported","Inflated")))[,
                                    c("Scenario","hat")]
dat=transform(merge(dat,hat),fmsy=fmsy/hat)              

ggplot(dat)+
  geom_hline(aes(yintercept=1))+
  geom_point(aes(year,fmsy,fill=Scenario),shape=21,size=3)+
  scale_fill_brewer(palette = "Set1")+
  facet_grid(name~.)+
  theme(legend.position="bottom")+
  theme_bw()+xlab("Year")+ylab(expression(F/F[MSY]))
```
**Figure `r iFig=iFig+1;iFig`.** Jackknife estimates of DFBETA for $F/F_{MSY}$ by year and CPUE series.

```{r influence_f, fig.height=8, fig.width=8}
dat=transform(rfDat,
              smsy=s.current/s.f0.1,
              Scenario=factor(scen,labels=c("Inflated","Reported")))[,
                                    c("Scenario","name","year","smsy")]
hat=transform(rfDatHat,
              hat=s.current/s.f0.1,
              Scenario=factor(X1,labels=c("Reported","Inflated")))[,
                                    c("Scenario","hat")]
dat=transform(merge(dat,hat),smsy=smsy/hat)              
ggplot(dat)+
  geom_hline(aes(yintercept=1))+
  geom_point(aes(year,smsy,fill=Scenario),shape=21,size=3)+
  scale_fill_brewer(palette = "Set1")+
  facet_grid(name~.)+
  theme_bw()+xlab("Year")+ylab(expression(SSB/SSB[MSY]))
```
**Figure `r iFig=iFig+1;iFig`.** Jackknife estimates of DFBETA for $B/B_{MSY}$ by year and CPUE series.

```{r influence_r, fig.height=8, fig.width=8}
dat=transform(rfDat,
              Scenario=factor(scen,labels=c("Inflated","Reported")))[,
                                    c("Scenario","name","year","r","rt")]
hat=transform(rfDatHat,
              rHat   =r,
              rtHat  =rt,
              Scenario=factor(X1,labels=c("Reported","Inflated")))[,
                                    c("Scenario","rHat","rtHat")]

dat=transform(merge(dat,hat),r=r/rHat,rt=rt/rtHat)              
ggplot(dat)+
  geom_hline(aes(yintercept=1))+
  geom_point(aes(year,r,fill=Scenario),shape=21,size=3)+
  scale_fill_brewer(palette = "Set1")+
  facet_grid(name~.)+
  theme_bw()+xlab("Year")+ylab("r")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.**  Jackknife estimates of DFBETA for population growth rate $r$ by year and CPUE series.

```{r influence_rt, fig.height=8, fig.width=8}

ggplot(dat)+
  geom_hline(aes(yintercept=1))+
  geom_point(aes(year,rt,fill=Scenario),shape=21,size=3)+
  scale_fill_brewer(palette = "Set1")+
  facet_grid(name~.)+
  theme_bw()+xlab("Year")+ylab(expression(r[recovery]))+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.**  Jackknife estimates of DFBETA for time taken to recover to $B_{MSY}$ (negative values indicate stock is above $B_{MSY}$) by year and CPUE series.


```{r}
load("/home/laurie/Desktop/tmp/rfs.RData")
names(rfs[[1]])=c("hat","mean","se","cv","bias","biasRel","cov","cor")
names(rfs[[2]])=c("hat","mean","se","cv","bias","biasRel","cov","cor")
```

```{r, fig.height=7,fig.width=9}
load("/home/laurie/Desktop/tmp/rfDat.RData")

dat=transmute(rfDat,
              name =name,
              ssmsy=s.current/s.f0.1,
              ffmsy=f.current/f.f0.1,
              r    =r,
              rt   =rt,
              residual=residual,
              year    =year,
              Scenario=factor(scen,labels=c("Reported","Inflated")))

ggplot(melt(dat,id=c("name","residual","year","Scenario")))+
  geom_point(aes(residual,value,fill=Scenario),shape=21,size=3)+
  facet_grid(variable~name,scale="free")+
  scale_fill_brewer(palette = "Set1")+
  theme_bw()+
  theme(legend.position="bottom")+
  ylab("Jackknife Estimate")+xlab("Residuals")

save(dat,file="/home/laurie/Desktop/tmp/dat.RData")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknifed estimates with residuals.


```{r, cor_ssbmsy, fig.height=9, fig.width=9}
library(reshape2)

ggplot(dcast(dat,year+name~Scenario,value.var="ssmsy",mean))+
   geom_point(aes(Reported,Inflated,fill=name),shape=21,size=4)+
   geom_smooth(aes(Reported,Inflated),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimates of population growth rate $B/B_{MSY}$ by year and CPUE series.


```{r, cor_ffmsy, fig.height=9, fig.width=9}
dat2=dcast(dat,year+name~Scenario,value.var="ffmsy",mean)

ggplot(dcast(dat,year+name~Scenario,value.var="ffmsy",mean))+
   geom_point(aes(Reported,Inflated,fill=name),shape=21,size=4)+
   geom_smooth(aes(Reported,Inflated),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimates of population growth rate $F/F_{MSY}$ by CPUE series.


```{r, cor_r, fig.height=9, fig.width=9}
library(reshape2)

ggplot(dcast(dat,year+name~Scenario,value.var="ssmsy",mean))+
   geom_point(aes(Reported,Inflated,fill=name),shape=21,size=4)+
   geom_smooth(aes(Reported,Inflated),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimates of population growth rate $r$ by CPUE series.


```{r, cor_rt, fig.height=9, fig.width=9}
library(reshape2)

ggplot(dcast(dat,year+name~Scenario,value.var="ssmsy",mean))+
   geom_point(aes(Reported,Inflated,fill=name),shape=21,size=4)+
   geom_smooth(aes(Reported,Inflated),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimates of time taken to recover to $B/B_{MSY}$ (negative values indicate stock is above $B_{MSY}$) by CPUE series.


```{r, corr_ssbmsy, fig.height=9, fig.width=9}
library(reshape2)

ggplot(dcast(dat,year+name~Scenario,value.var="ssmsy",mean))+
   geom_point(aes(rank(Reported),rank(Inflated),fill=name),shape=21,size=4)+
   geom_smooth(aes(rank(Reported),rank(Inflated)),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimate ranks of population growth rate $B/B_{MSY}$ by year and CPUE series.


```{r, corr_ffmsy, fig.height=9, fig.width=9}
ggplot(dcast(dat,year+name~Scenario,value.var="ffmsy",mean))+
   geom_point(aes(rank(Reported),rank(Inflated),fill=name),shape=21,size=4)+
   geom_smooth(aes(rank(Reported),rank(Inflated)),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimate ranks of population growth rate $F/F_{MSY}$ by CPUE series.


```{r, corr_r, fig.height=9, fig.width=9}
ggplot(dcast(dat,year+name~Scenario,value.var="ssmsy",mean))+
   geom_point(aes(rank(Reported),rank(Inflated),fill=name),shape=21,size=4)+
   geom_smooth(aes(rank(Reported),rank(Inflated)),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimate ranks of population growth rate $r$ by CPUE series.


```{r, corr_rt, fig.height=9, fig.width=9}
ggplot(dcast(dat,year+name~Scenario,value.var="ssmsy",mean))+
   geom_point(aes(rank(Reported),rank(Inflated),fill=name),shape=21,size=4)+
   geom_smooth(aes(rank(Reported),rank(Inflated)),se=FALSE,method=lm)+
   scale_fill_brewer(palette = "Set1")+
   facet_wrap(~name,scale="free")+
   theme_bw()+theme(legend.position="none")
```
**Figure `r iFig=iFig+1;iFig`.** Comparison of jackknife estimate ranks of time taken to recover to $B/B_{MSY}$ (negative values indicate stock is above $B_{MSY}$) by CPUE series.

```{r}
delta<-function(z,t){
  if (t<0)
    (1-exp(-z))/z
  else
    exp(-z*t/12)}

butterVul<-function(paa,stk,waa){
    
  ag=dimnames(paa)$age
  yr=dimnames(paa)$year 
  
  sp=paa[ag,yr]
  hv=harvest(stk)[ag,yr]
  cn=catch.n(stk)[ag,yr]
  
  #numerator
  nm =apply(sp%*%hv%/%cn,c(1,6),sum)

  #denominator
  dn=hv%/%apply(hv,2:6,max)
  dn=apply(dn==1,1:6,as.numeric)
  dn[dn!=1]=NA
  dn=dn%*%hv%*%sp%/%cn
  dn=apply(dn,c(2:6),mean,na.rm=TRUE)
  dn=apply(dn,c(3:6),sum,na.rm=TRUE)
  
  res=nm%/%dn
  res%/%apply(res,2,max)}
```

```{r}
source('~/Desktop/flr/diags/R/read-VPA2Box-FLIndices.R')
dirJK ="/home/laurie/Desktop/SCRS/workshops/vpa/sessions/data"
load(file.path(dirJK,"jk.RData"))
stks=jk[[1]][[1]]
qs  =jk[[1]][[2]]
names(qs)=c("iter","name","q")

idx=readVP2BoxIndices("/home/laurie/Desktop/kobe/inputs/bfte/2014/vpa/reported/med/bfte2014.d1")
names(idx)=c('ESPMarTrap','JLL EastMed','Nor PS','JP LL NEA','SP BB1','SP BB2','SP BB3')
sel.pattern(idx[[3]])[]=1
  
dgs=diagsVpa2box("/home/laurie/Desktop/kobe/inputs/bfte/2014/vpa/reported/med/MINUS0.R")

sim=data.frame(iter=seq(dim(dgs)[1]),dgs[,1:2])
qs =merge(sim,qs,by=c("name","iter"))
qs =qs[do.call(order,list(qs[,"year"])),]
qs =qs[do.call(order,list(qs[,c("name")])),]
```

```{r}
chk=ddply(dgs,.(name), with, {

  stk=stks[[1]]
  paa=catch.n( idx[[name[1]]])[,dimnames(index(idx[[name[1]]]))$year]
  waa=catch.wt(idx[[name[1]]])[,dimnames(index(idx[[name[1]]]))$year]

  if (index(idx[[name[1]]])@units=="number") waa[]=1

  if (type(idx[[name[1]]])=="butt") 
     vl =butterVul(paa,stk)
  else if (type(idx[[name[1]]])=="fixed")
     vl=sel.pattern(idx[[name[1]]])
  
  aa=stock.n(stk)[dimnames(vl)$age,dimnames(index(idx[[name[1]]]))$year]%*%waa[dimnames(vl)$age,]

  hat=apply(vl%*%aa%*%
           delta(harvest(stk)[dimnames(vl)$age,dimnames(index(idx[[name[1]]]))$year]+
                       m(stk)[dimnames(vl)$age,dimnames(index(idx[[name[1]]]))$year],-1),2,sum)*q

  data.frame(hat=hat,year=dimnames(index(idx[[name[1]]]))$year)})

rsdl=merge(chk,dgs[,c("name","year","y2","x2")],by=c("name","year"))
         
p1=ggplot(rsdl)+
  geom_point(aes(hat,y2,fill=name),shape=21)+
  facet_wrap(~name,scale="free")
  
p2=ggplot(subset(rsdl,name=="JLL EastMed"))+
  geom_point(aes(hat,x2),col="red")+
  geom_point(aes(y2, x2),col="blue")
```

```{r}
res=ddply(qs,.(name,iter,year), with, {
  paa=catch.n( idx[[name]])[,dimnames(index(idx[[name]]))$year]
  waa=catch.wt(idx[[name]])[,dimnames(index(idx[[name]]))$year]
  
  if (index(idx[[name[1]]])@units=="number") waa[]=1

  stk=iter(stks[[2]],iter)
  if (type(idx[[name[1]]])=="butt") 
     vl =butterVul(paa,stk)
  else if (type(idx[[name[1]]])=="fixed")
     vl=sel.pattern(idx[[name[1]]])

  aa=stock.n(stk)[dimnames(vl)$age,dimnames(index(idx[[name]]))$year]%*%waa[dimnames(vl)$age,]
  
  hat=apply(vl%*%aa%*%
           delta(harvest(stk)[dimnames(vl)$age,dimnames(index(idx[[name]]))$year]+
                       m(stk)[dimnames(vl)$age,dimnames(index(idx[[name]]))$year],-1),2,sum)*q
  
  data.frame(hat=hat[ac(year)],q=q)})

rsdl=merge(res,dgs[,c("name","year","y2","x2")],by=c("name","year"))
         
p1=ggplot(rsdl)+
  geom_point(aes(hat,y2,fill=name),shape=21)+
  facet_wrap(~name,scale="free")

p2=ggplot(rsdl)+
  geom_point(aes(year,log(x2/hat)),col="red")+
  geom_point(aes(year,log(x2/y2)),col="blue")+
  facet_wrap(~name,scale="free")
```

```{r}
library(reshape2)
ggplot(melt(rsdl[,c("name","x2","y2","hat")],id=c("name","x2")))+
  geom_boxplot(aes(name, log(x2/value), fill=variable),outlier.size=2.5)+
  scale_fill_manual("Residuals",
                      labels = c("Model", "Prediction"),
                      values = c("#E69F00", "#D55E00"))+
  theme_bw()+xlab("Fleet")+ylab("Residual")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Prediction residuals by CPUE series for the reported catch Scenario.

```{r}
ggplot(melt(subset(rsdl,as.numeric(ac(year))>2005)[,                                c("name","x2","y2","hat","year")],id=c("name","year","x2")),
          aes(factor(year), log(x2/value),fill=variable)) +
  geom_boxplot() +
  geom_point(position=position_dodge(width=0.75),aes(group=variable,col=name),size=2.5)+
  scale_colour_brewer(palette = "Set1")+
  scale_fill_manual("Residuals",
                      labels = c("Model", "Prediction"),
                      values = c("#E69F00", "#D55E00"))+
  theme_bw()+xlab("Year")+ylab("Residual")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Prediction residuals by year for the reported catch Scenario.

```{r}
source('~/Desktop/flr/diags/R/read-VPA2Box-FLIndices.R')
dirJK ="/home/laurie/Desktop/SCRS/workshops/vpa/sessions/data"
load(file.path(dirJK,"jk.RData"))
stks=jk[[2]][[1]]
qs  =jk[[2]][[2]]
names(qs)=c("iter","name","q")

idx=readVP2BoxIndices("/home/laurie/Desktop/kobe/inputs/bfte/2014/vpa/inflated/med/bfte2014.d1")
names(idx)=c('ESPMarTrap','JLL EastMed','Nor PS','JP LL NEA','SP BB1','SP BB2','SP BB3')
sel.pattern(idx[[3]])[]=1
  
dgs=diagsVpa2box("/home/laurie/Desktop/kobe/inputs/bfte/2014/vpa/inflated/med/MINUS0.R")

sim=data.frame(iter=seq(dim(dgs)[1]),dgs[,1:2])
qs =merge(sim,qs,by=c("name","iter"))
qs =qs[do.call(order,list(qs[,"year"])),]
qs =qs[do.call(order,list(qs[,c("name")])),]

chk=ddply(dgs,.(name), with, {

  paa=catch.n( idx[[name[1]]])[,dimnames(index(idx[[name[1]]]))$year]
  waa=catch.wt(idx[[name[1]]])[,dimnames(index(idx[[name[1]]]))$year]

  if (index(idx[[name[1]]])@units=="number") waa[]=1

  stk=stks[[1]]
  
  if (type(idx[[name[1]]])=="butt") 
     vl =butterVul(paa,stk)
  else if (type(idx[[name[1]]])=="fixed")
     vl=sel.pattern(idx[[name[1]]])
  
  aa=stock.n(stk)[dimnames(vl)$age,dimnames(index(idx[[name[1]]]))$year]%*%waa[dimnames(vl)$age,]

  hat=apply(vl%*%aa%*%
           delta(harvest(stk)[dimnames(vl)$age,dimnames(index(idx[[name[1]]]))$year]+
                       m(stk)[dimnames(vl)$age,dimnames(index(idx[[name[1]]]))$year],-1),2,sum)*q

  data.frame(hat=hat,year=dimnames(index(idx[[name[1]]]))$year)})

rsdl=merge(chk,dgs[,c("name","year","y2","x2")],by=c("name","year"))
         
p1=ggplot(rsdl)+
  geom_point(aes(hat,y2,fill=name),shape=21)+
  facet_wrap(~name,scale="free")
  
p2=ggplot(subset(rsdl,name=="JLL EastMed"))+
  geom_point(aes(hat,x2),col="red")+
  geom_point(aes(y2, x2),col="blue")
```

```{r}
res=ddply(qs,.(name,iter,year), with, {
  paa=catch.n( idx[[name]])[,dimnames(index(idx[[name]]))$year]
  waa=catch.wt(idx[[name]])[,dimnames(index(idx[[name]]))$year]
  
  if (index(idx[[name[1]]])@units=="number") waa[]=1

  stk=iter(stks[[2]],iter)
  if (type(idx[[name[1]]])=="butt") 
     vl =butterVul(paa,stk)
  else if (type(idx[[name[1]]])=="fixed")
     vl=sel.pattern(idx[[name[1]]])

  aa=stock.n(stk)[dimnames(vl)$age,dimnames(index(idx[[name]]))$year]%*%waa[dimnames(vl)$age,]
  
  hat=apply(vl%*%aa%*%
           delta(harvest(stk)[dimnames(vl)$age,dimnames(index(idx[[name]]))$year]+
                       m(stk)[dimnames(vl)$age,dimnames(index(idx[[name]]))$year],-1),2,sum)*q
  
  data.frame(hat=hat[ac(year)],q=q)})

rsdl=merge(res,dgs[,c("name","year","y2","x2")],by=c("name","year"))
         
p1=ggplot(rsdl)+
  geom_point(aes(hat,y2,fill=name),shape=21)+
  facet_wrap(~name,scale="free")

p2=ggplot(rsdl)+
  geom_point(aes(year,log(x2/hat)),col="red")+
  geom_point(aes(year,log(x2/y2)),col="blue")+
  facet_wrap(~name,scale="free")
```

```{r}
library(reshape2)
ggplot(melt(rsdl[,c("name","x2","y2","hat")],id=c("name","x2")))+
  geom_boxplot(aes(name, log(x2/value), fill=variable),outlier.size=2.5)+
  scale_fill_manual("Residuals",
                      labels = c("Model", "Prediction"),
                      values = c("#E69F00", "#D55E00"))+
  theme_bw()+xlab("Fleet")+ylab("Residual")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Prediction residuals by CPUE series for the inflated catch Scenario.

```{r}
ggplot(melt(subset(rsdl,year>=2005)[,c("name","x2","y2","hat","year")],id=c("name","year","x2")),
          aes(factor(year), log(x2/value),fill=variable)) +
  geom_boxplot() +
  geom_point(position=position_dodge(width=0.75),aes(group=variable,col=name),size=2.5)+
  scale_colour_brewer(palette = "Set1")+
  scale_fill_manual("Residuals",
                      labels = c("Model", "Prediction"),
                      values = c("#E69F00", "#D55E00"))+
  theme_bw()+xlab("Year")+ylab("Residual")+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1;iFig`.** Prediction residuals by year for the inflated catch Scenario.


\newpage
#Tables

```{r}
library(pander)
pander::panderOptions('table.split.table', 350)

load("/home/laurie/Desktop/tmp/rfs.RData")
```

**Table `r iTab=iTab+1; iTab`** Summary of reported catch Scenario summary statistics. 
```{r}
pander::pandoc.table(model.frame(rfs[[1]][1:6])[,-2], style="rmarkdown")
```

```{r, eval=FALSE}
pander::pandoc.table(rfs[[1]][[8]][drop=T], style="rmarkdown")
```

**Table `r iTab=iTab+1; iTab`** Summary of inflated catch Scenario summary statistics.
```{r}
pander::pandoc.table(model.frame(rfs[[2]][1:6])[,-2], style="rmarkdown")
```

```{r, eval=FALSE}
pander::pandoc.table(rfs[[2]][[8]][drop=T], style="rmarkdown")
```


```{r, eval=FALSE}
library(FLCore)
library(ggplotFL)
library(FLife)

source('~/Desktop/flr/diags/R/read-VPA2Box-FLIndices.R')


m=c(0.49,0.24,0.24,0.24,0.24,0.20,0.175,0.15,0.125,0.10) 

u=readVP2BoxIndices("/home/laurie/Desktop/SCRS/bftAss/bft2017/inputs/2017/bfte2017.d1")
names(u)=c("MarPorTrap","JLL EastMed","JP LL NEA1","JP LL NEA2","SP BB1","SP BB2","Aerial","larval survey")
u=FLQuants(llply(u, index))

vpa=readVPA2Box("/home/laurie/Desktop/SCRS/bftAss/bft2017/inputs/2017/bfte2017.c1")


bd=biodyn(catch=catch(vpa))
params(bd)["k"]=mean(catch(vpa))*12.5
params(bd)["p"]=0.0000001
bd=fwd(bd,catch=catch(vpa))

setParams(bd)=u
setControl(bd)=params(bd)

control(bd)[paste("q",1:7,sep=""),c("min","max")]=
             control(bd)[paste("q",1:7,sep=""),c("min","max")]*c(0.1,10)
control(bd)[paste("sigma",1:7,sep=""),c("min","max")]=
  control(bd)[paste("q",1:7,sep=""),c("min","max")]*c(0.1,10)
control(bd)[paste("q",1:7,sep=""),"phase"]=2
control(bd)[paste("q",1:7,sep=""),"phase"]=-2

bd=fit(bd,u)

ss1=sum(diags(bd)[,"residual"]^2,na.rm=TRUE)
ss2=sum(diags(asp2013)[,"residual"]^2,na.rm=TRUE)

plot(mpb:::biodyns(list("biodyn"=bd,"aspic"=as(asp2013,"biodyn"))))+
  theme_bw()
```
**Figure `r iFig=iFig+1; iFig`.** 



```
